---
title: "`r lg[['0_main_title']]`"
subtitle: "`r lg[['0_sub_title_twin']]`"
output: word_document
params:
  lg: NULL
---


# `r lg[['0_title_device']]`

```{r, echo=FALSE,warning=FALSE,comment="",message=FALSE}

##Create a table with gear names, selective device, codend mesh size, 
#headline length

  df<-data %>%
  group_by(gear_label) %>%
  summarise(type=unique(gear_type),sel=unique(selective_device),mesh=unique(mesh_gauge_codend_mm),length=unique(headline_cumulative_length)) %>% as.data.frame()
  
  names(df)<-c("",lg[["0_gear"]],lg[["0_selective_device"]],lg[["0_codend_mesh"]],lg[["0_headline"]])
  
kable(df)

```

# 1.`r lg[['1_title']]`

### `r lg[['1_subtitle_vessel_trip']]`

```{r, echo=FALSE,warning=FALSE,comment="",message=FALSE}

##Create a table with vessels and trips names for each vesselxtrip: 
#station's numbers, dates

  df<-data %>%
  group_by(project,vessel_identifier,vessel_name,trip_code) %>%
  summarise(NombreOP=length(unique(station_number)),Debut=unique(departure_date_time),Fin=unique(return_date_time)) %>% as.data.frame()
  

  names(df)<-c(lg[["1_project"]],lg[["1_ID_vessel"]],lg[["1_vessel"]],lg[["1_ID_trip"]],lg[["1_FO"]],lg[["1_start_date"]],lg[["1_end_date"]])
  
kable(df)

```


### `r lg[['1_subtitle_maps']]`
```{r, echo=FALSE,warning=FALSE,comment="",message=FALSE,fig.width=30,fig.height=12}

Maps

```

### `r lg[['1_subtitle_fishing_conditions']]`

```{r, echo=FALSE,warning=FALSE,fig.cap=lg[['1_duration_caption']],comment="",message=FALSE,fig.asp=0.5}

tab_OP<- data %>% group_by(project,vessel_identifier,trip_code,station_number)%>%
    summarize(fishing_duration=unique(fishing_duration),gear_depth=unique(gear_depth),
              wind_force_beaufort=unique(wind_force_beaufort),gear_speed=unique(gear_speed),sea_state=unique(sea_state))

nrow_info<-nrow(tab_OP)

if(length(which(is.na(tab_OP$fishing_duration)==FALSE))>0){
  ggplot(tab_OP,aes(y=fishing_duration))+
  geom_boxplot(width=0.5)+labs(y=lg[["1_duration_labs"]])+
  geom_point(aes(x=0,y=mean(fishing_duration)),shape=4) + 
  theme(legend.position = "None",axis.text=element_text(size=8),
        axis.title=element_text(size=10),axis.text.x=element_blank())+
    xlab("")
}

nNA<-length(which(is.na(tab_OP$fishing_duration)==T))
nrow_info<-nrow(tab_OP)
if(nNA>0){cat(sprintf(lg[["1_missing_values"]],nNA,nrow_info))}
  
```

```{r, echo=FALSE,warning=FALSE,fig.cap=lg[['1_depth_caption']],comment="",message=FALSE,fig.asp=0.5}


if(length(which(is.na(tab_OP$gear_depth)==FALSE))>0){
  ggplot(tab_OP,aes(y=gear_depth))+
  geom_boxplot(width=0.5)+labs(y=lg[["1_depth_labs"]])+
  geom_point(aes(x=0,y=mean(gear_depth)),shape=4) + 
  theme(legend.position = "None",axis.text=element_text(size=8),
        axis.title=element_text(size=10),axis.text.x=element_blank())+
    xlab("")
}

nNA<-length(which(is.na(tab_OP$gear_depth)==T))
if(nNA>0){cat(sprintf(lg[["1_missing_values"]],nNA,nrow_info))}
  
  cat("\n   \n")
  cat("\n   \n") 
```

```{r, echo=FALSE,warning=FALSE,fig.cap=lg[['1_speed_caption']],comment="",message=FALSE,fig.asp=0.5}

if(length(which(is.na(tab_OP$gear_speed)==FALSE))>0){
  
    ggplot(tab_OP,aes(y=gear_speed))+
  geom_boxplot(width=0.5)+labs(y=lg[["1_speed_labs"]])+
  geom_point(aes(x=0,y=mean(gear_speed)),shape=4) + 
  theme(legend.position = "None",axis.text=element_text(size=8),
        axis.title=element_text(size=10),axis.text.x=element_blank())+
    xlab("")
  
}

nNA<-length(which(is.na(tab_OP$gear_speed)==T))
if(nNA>0){cat(sprintf(lg[["1_missing_values"]],nNA,nrow_info))}
  
```
```{r, echo=FALSE,warning=FALSE,fig.cap=lg[['1_sea_state_caption']],comment="",message=FALSE,fig.asp=0.5}

if(length(which(is.na(tab_OP$sea_state)==FALSE))>0){
  
    ggplot(tab_OP,aes(y=sea_state))+
  geom_boxplot(width=0.5)+labs(y=lg[["1_sea_state_labs"]])+
  geom_point(aes(x=0,y=mean(sea_state)),shape=4) + 
  theme(legend.position = "None",axis.text=element_text(size=8),
        axis.title=element_text(size=10),axis.text.x=element_blank())+
    xlab("")
  
}

nNA<-length(which(is.na(tab_OP$gear_speed)==T))
if(nNA>0){cat(sprintf(lg[["1_missing_values"]],nNA,nrow_info))}
  
```

```{r, echo=FALSE,warning=FALSE,fig.cap=lg[['1_wind_caption']],comment="",message=FALSE,fig.asp=0.5}

if(length(which(is.na(tab_OP$wind_force_beaufort)==FALSE))>0){

      ggplot(tab_OP,aes(y=wind_force_beaufort))+
  geom_boxplot(width=0.5)+labs(y=lg[["1_wind_labs"]])+
  geom_point(aes(x=0,y=mean(wind_force_beaufort)),shape=4) + 
  theme(legend.position = "None",axis.text=element_text(size=8),
        axis.title=element_text(size=10),axis.text.x=element_blank())+
    xlab("")
}

nNA<-length(which(is.na(tab_OP$wind_force_beaufort)==T))
if(nNA>0){cat(sprintf(lg[["1_missing_values"]],nNA,nrow_info))}
 

```


```{r, echo=FALSE,warning=FALSE,fig.cap=lg[['1_seabed_caption']],comment="",message=FALSE,fig.asp=0.5}

#fishing conditions /fishing operation : categorical variables

tab_OP2<- data %>% group_by(project,vessel_identifier,trip_code,station_number)%>%
    summarize(seabed_features=unique(seabed_features),
              wind_cardinal_direction=unique(wind_cardinal_direction),diurnal_operation=unique(diurnal_operation))

nrow_info2<-nrow(tab_OP2)

if(length(which(is.na(tab_OP2$seabed_features)))==0){
ggplot(tab_OP2,aes(x=seabed_features))+ geom_bar(stat = 'count',width=0.2) +
 labs(y = lg[["1_FO"]],x=lg[["1_seabed_labs"]])+
  theme(legend.position = "None",axis.text=element_text(size=8),
        axis.title=element_text(size=10))
}

nNA<-length(which(is.na(tab_OP2$seabed_features)==T))
if(nNA>0){cat(sprintf(lg[["1_missing_values"]],nNA,nrow_info2))}
 
```

```{r, echo=FALSE,warning=FALSE,fig.cap=lg[['1_wind_dir_caption']],comment="",message=FALSE,fig.asp=0.5}

if(length(which(is.na(tab_OP2$wind_cardinal_direction)))==0){
ggplot(tab_OP2,aes(x=wind_cardinal_direction))+ geom_bar(stat = 'count',width=0.2) +
 labs(y = lg[["1_FO"]],x=lg[["1_wind_dir_labs"]])+
  theme(legend.position = "None",axis.text=element_text(size=8),
        axis.title=element_text(size=10))
}

nNA<-length(which(is.na(tab_OP2$wind_cardinal_direction)==T))
if(nNA>0){cat(sprintf(lg[["1_missing_values"]],nNA,nrow_info2))}
```


```{r, echo=FALSE,warning=FALSE,fig.cap=lg[['1_day_caption']],comment="",message=FALSE,fig.asp=0.5}
if(length(which(is.na(tab_OP2$diurnal_operation)))==0){
tab_OP2$diurnal_operation<-factor(tab_OP2$diurnal_operation,levels=c("Y","N"),labels=c(lg[["1_day"]],lg[["1_night"]]))

ggplot(tab_OP2,aes(x=diurnal_operation))+ geom_bar(stat = 'count',width=0.2) +
 labs(y = lg[["1_FO"]],x="")+
  theme(legend.position = "None",axis.text=element_text(size=8),
        axis.title=element_text(size=10))
}

nNA<-length(which(is.na(tab_OP2$diurnal_operation)==T))
if(nNA>0){cat(sprintf(lg[["1_missing_values"]],nNA,nrow_info2))}
  
```



### `r lg[['1_subtitle_fishing_summary']]`

```{r, echo=FALSE,warning=FALSE,comment="",message=FALSE}

varC<-c("fishing_duration","gear_depth","gear_speed","wind_force_beaufort","sea_state")

df<-data.frame(Variable=c(lg[["1_duration_labs"]],lg[["1_depth_labs"]],lg[["1_speed_labs"]],lg[["1_wind_labs"]],lg[["1_sea_state_labs"]]))  
df$min<-apply(tab_OP[,varC],2,"min")
df$max<-apply(tab_OP[,varC],2,"max")
df$mean<-apply(tab_OP[,varC],2,"mean")
df$median<-apply(tab_OP[,varC],2,"median")

df$diff<-0

df[,-1]<-round(df[,-1],1)

df$nNA<-apply(tab_OP[,varC],2,function(x){length(which(is.na(x)==TRUE))})


# #Pour la capture totale et le temps de tri
# var<-c("catch_weight","sorting_time")
# 
# df2<-data.frame(Variable=c("Poids de la capture (kg)","Durée de tri (min)"))  
# df2$min<-apply(tab_capture[,var],2,"min",na.rm=T)
# df2$max<-apply(tab_capture[,var],2,"max",na.rm=T)
# df2$mean<-apply(tab_capture[,var],2,"mean",na.rm=T)
# df2$median<-apply(tab_capture[,var],2,"median",na.rm=T)
# 
# 
# df2$diff<-data.frame(tab_capture) %>%
#   summarize(catch_weight=mean(catch_weight[gear_label=="TEST"]-catch_weight[gear_label=="STD"],na.rm=T),
#             sorting_time=mean(sorting_time[gear_label=="TEST"]-sorting_time[gear_label=="STD"],na.rm=T))%>%as.numeric()
# 
# df2[,-1]<-round(df2[,-1],1)
# df2$nNA<-apply(tab_capture[,var],2,function(x){length(which(is.na(x)==TRUE))})
# 
# df<-rbind(df,df2)

if(sum(df$nNA>0)){
names(df)<-c("","Min","Max",lg[["1_mean"]],lg[["1_median"]],lg[["1_difference"]],lg[["1_values"]])

kable(df)
}else{df<-select(df,-nNA)
names(df)<-c("","Min","Max",lg[["1_mean"]],lg[["1_median"]],lg[["1_difference"]])
kable(df)
}

```



# 2. `r lg[['2_title']]`

## 2.1. `r lg[['2_1_subtitle']]`

### `r lg[['2_1_subtitle_catch_weight']]`

```{r, echo=FALSE,warning=FALSE,fig.cap=lg[['2_1_catch_caption']],comment="",message=FALSE,fig.asp=0.5}

#Comparison of catches weights, sorting time, discards weights / fishing operation:

##sorting time calculation
data$sorting_start_date_time<-as.POSIXct(data$sorting_start_date_time,format="%Y-%m-%d %H:%M:%S")
data$sorting_end_date_time<-as.POSIXct(data$sorting_end_date_time,format="%Y-%m-%d %H:%M:%S")
data$sorting_time<-with(data,difftime(sorting_end_date_time,sorting_start_date_time,units="mins"))

tab_capture<- data %>% 
  group_by(project,vessel_identifier,trip_code,station_number,gear_label)%>%
  summarize(catch_weight=unique(catch_weight),sorting_time=unique(sorting_time),
              discard_weight=unique(discard_weight))

nrow_info<- nrow(tab_capture)

if(length(which(is.na(tab_capture$catch_weight)==FALSE))>0){
  
  ggplot(tab_capture,aes(y=catch_weight,x=gear_label))+
  geom_boxplot(width=0.5,aes(fill=gear_label))+labs(y=lg[["2_1_catch_labs"]])+
   stat_summary(fun=mean, geom="point", shape=4, position = position_dodge(0.75),lwd=2)+
  theme(legend.position = "None",axis.text=element_text(size=8),
        axis.title=element_text(size=10))+
    xlab("")
}
nNA<-length(which(is.na(tab_capture$catch_weight)==T))
if(nNA>0){cat(sprintf(lg[["1_missing_values"]],nNA,nrow_info))}
 
```

### `r lg[['2_1_subtitle_sorting']]`

```{r, echo=FALSE,warning=FALSE,fig.cap=lg[['2_1_sorting_caption']],comment="",message=FALSE,fig.asp=0.5}

if(length(which(is.na(tab_capture$sorting_time)==FALSE))>0){
  
  ggplot(tab_capture,aes(y=sorting_time,x=gear_label))+
  geom_boxplot(width=0.5,aes(fill=gear_label))+labs(y=lg[["2_1_sorting_labs"]])+
   stat_summary(fun=mean, geom="point", shape=4, position = position_dodge(0.75),lwd=2)+
  theme(legend.position = "None",axis.text=element_text(size=8),
        axis.title=element_text(size=10))+
    xlab("")
}
nNA<-length(which(is.na(tab_capture$sorting_time)==T))
if(nNA>0){cat(sprintf(lg[["1_missing_values"]],nNA,nrow_info))}

## Test sorting duration?

```


```{r, echo=FALSE,warning=FALSE,comment="",message=FALSE}

#For each FO and catch category, weight difference TEST-STD:
tab_diff<-tab_capture %>% group_by(project,vessel_identifier,trip_code,station_number)%>%
  summarize(weight_DIS_STD=sorting_time[gear_label=="STD"],weight_DIS_TEST=sorting_time[gear_label=="TEST"],
            diff_DIS=sorting_time[gear_label=="TEST"]-sorting_time[gear_label=="STD"])

diff_DIS<-tab_diff$diff_DIS

#Shapiro-Wilk test for normality
test1<-tryCatch(shapiro.test(diff_DIS), error = function(e){"e"})

#if no error:
if(class(test1) =="htest"){
  
  #If normality not rejected (p-value >0.05), Student test:
  if(test1$p.value > 0.05){
    test2<-tryCatch(t.test(x=diff_DIS,mu=0) , error = function(e){"e"})
  }
  #if normality rejected (p-value <= 0.05), Mann-Whitney/Wilcoxon test:
  if(test1$p.value <= 0.05){
    test2<-tryCatch(wilcox.test(diff_DIS, paired =F, correct = T, exact = F), error = function(e){"e"})
  }
  
  if(class(test2) == "htest"){#if no error
    
    if(test2$p.value<=0.05){
      
      cat(lg[["2_1_sorting_test_diff"]],"\n")
 }else{ cat(lg[["2_1_sorting_test_nodiff"]],"\n")}
      
  }    
    
 
  pvalue<-round(test2$p.value,4)
  if(test1$p.value <= 0.05){
     med<-  abs(round(median(diff_DIS),3))
    sign<-c(lg[["2_1_less"]],lg[["2_1_more"]])[as.numeric(eval(median(diff_DIS)>0))+1]
    
        cat(sprintf(lg[["2_1_sorting_test_med"]],med,sign,pvalue) )
      }
  
  if(test1$p.value > 0.05){
     mean<-  abs(round(mean(diff_DIS),3))
    sign<-c(lg[["2_1_less"]],lg[["2_1_more"]])[as.numeric(eval(mean(diff_DIS)>0))+1]
    
       cat(sprintf(lg[["2_1_sorting_test_mean"]],med,sign,pvalue) )
      }
   
}

```


### `r lg[['2_1_subtitle_sorting_variation']]`

```{r, echo=FALSE,warning=FALSE,comment="",message=FALSE}

#Variation rate (TEST-STD)/STD
Tot_TEST<-sum(tab_diff$weight_DIS_TEST)
Tot_STD<-sum(tab_diff$weight_DIS_STD)

Var_Rate<-(Tot_TEST-Tot_STD)/Tot_STD*100

if(is.na(Var_Rate)==FALSE){
  sign<-c(lg[["2_1_decrease"]] ,lg[["2_1_increase"]])[as.numeric(eval(Var_Rate>0))+1]
  rate<-abs(round(Var_Rate,2))
cat(sprintf(lg[["2_1_sorting_var1"]],sign,rate))

Var_Rate2<-with(tab_diff,diff_DIS/weight_DIS_STD)*100
   rate<-abs(round(mean(Var_Rate2),2))
cat(sprintf(lg[["2_1_sorting_var2"]],sign,rate))

}
```


### `r lg[['2_1_subtitle_discard_weight']]`

```{r, echo=FALSE,warning=FALSE,message=FALSE,fig.width=3}

if(length(which(is.na(tab_capture$discard_weight)))==0){
  ggplot(tab_capture,aes(y=discard_weight,x=gear_label,fill=gear_label))+
  geom_boxplot(width=0.5)+labs(y = lg[["2_1_discard_weight_labs"]])+
  xlab("Engin")+
    theme_light()+
    theme(legend.position = "None",axis.text=element_text(size=8),
        axis.title=element_text(size=10))+
  stat_summary(fun=mean, geom="point", shape=4, position = position_dodge(0.75),lwd=2)
}

# ##Comparaison des poids pêchés sur le total de la liste
# 
# #Table des poids pour chaque Num_Trait, Engin, Fraction:
# tab_catch_list<-TAB%>%
#   group_by(project,vessel_identifier,trip_code,station_number,gear_label,catch_category)%>%
#   summarize(weight=sum(weight,na.rm=T))%>% as.data.frame()
# 
# tab_catch_list<-as.data.frame(complete(tab_catch_list,nesting(project,vessel_identifier,trip_code,station_number),gear_label,catch_category, fill = list(weight = 0)))
# 
# ##Boxplots du poids des rejets 
# ggplot(filter(tab_catch_list,catch_category=="DIS"),aes(y=weight,x=gear_label,fill=gear_label))+
#   geom_boxplot(width=0.5)+labs(y = "Poids des rejets ciblés par capture (Kg)")+
#   theme(legend.position = "None",axis.text=element_text(size=12),
#         axis.title=element_text(size=14))+
#   stat_summary(fun=mean, geom="point", shape=4, position = position_dodge(0.75),lwd=2)


```


```{r, echo=FALSE,warning=FALSE,comment="",message=FALSE}

#Pour chaque OP et fraction, difference de biomasse TEST-STD:

tab_diff<-tab_capture %>% group_by(project,vessel_identifier,trip_code,station_number)%>%
  summarize(weight_DIS_STD=discard_weight[gear_label=="STD"],weight_DIS_TEST=discard_weight[gear_label=="TEST"],
            diff_DIS=discard_weight[gear_label=="TEST"]-discard_weight[gear_label=="STD"])

diff_DIS<-tab_diff$diff_DIS

#Shapiro-Wilk normality test
test1<-tryCatch(shapiro.test(diff_DIS), error = function(e){"e"})

#if no "error":
if(class(test1) =="htest"){
  
  #If normality not rejected (p-value >0.05), Student test:
  if(test1$p.value > 0.05){
    test2<-tryCatch(t.test(x=diff_DIS,mu=0) , error = function(e){"e"})
  }
  #If normality rejected (p-value <= 0.05), Mann-Whitney/Wilcoxon test:
  if(test1$p.value <= 0.05){
    test2<-tryCatch(wilcox.test(diff_DIS, paired =F, correct = T, exact = F), error = function(e){"e"})
  }
  
  if(class(test2) == "htest"){#if no error
    
    if(test2$p.value<=0.05){
      
      cat(lg[["2_1_discard_test_diff"]],"\n")
 }else{ cat(lg[["2_1_discard_test_nodiff"]],"\n")}
      
  }    
      
  if(test1$p.value <= 0.05){
        
    med<-abs(round(median(diff_DIS),3))
    sign<-c(lg[["2_1_less"]],lg[["2_1_more"]])[as.numeric(eval(median(diff_DIS)>0))+1]
    pvalue<-round(test2$p.value,4)
    cat(sprintf(lg[["2_1_discard_test_med"]],med,sign,pvalue))
      }
  
  if(test1$p.value > 0.05){
   mean<-abs(round(mean(diff_DIS),3))
    sign<-c(lg[["2_1_less"]],lg[["2_1_more"]])[as.numeric(eval(mean(diff_DIS)>0))+1]
    pvalue<-round(test2$p.value,4)
    cat(sprintf(lg[["2_1_discard_test_mean"]],mean,sign,pvalue))
      }
   
}

```


### `r lg[['2_1_subtitle_discard_variation']]`

```{r, echo=FALSE,warning=FALSE,comment="",message=FALSE}

#Variation rate (TEST-STD)/STD
Tot_TEST<-sum(tab_diff$weight_DIS_TEST)
Tot_STD<-sum(tab_diff$weight_DIS_STD)

Var_Rate<-(Tot_TEST-Tot_STD)/Tot_STD*100

sign<-c("diminution" ,"augmentation")[as.numeric(eval(Var_Rate>0))+1]
rate<-abs(round(Var_Rate,2))
cat(sprintf(lg[["2_1_discard_var1"]],sign,rate))

Var_Rate2<-with(tab_diff,diff_DIS/weight_DIS_STD)*100
  
sign<-c("diminution" ,"augmentation")[as.numeric(eval(mean(Var_Rate2)>0))+1]
rate<-abs(round(mean(Var_Rate2),2))
cat(sprintf(lg[["2_1_discard_var2"]],sign,rate))

```



## 2.2. `r lg[["2_2_subtitle"]]`

### `r lg[["2_2_list_LAN"]]`
```{r, echo=FALSE,warning=FALSE,comment="",message=FALSE}
List_LAN<-unique(filter(data,catch_category=="LAN")$species)
cat(List_LAN,sep=", ")

```

### `r lg[["2_2_list_DIS"]]`
```{r, echo=FALSE,warning=FALSE,comment="",message=FALSE}
List_DIS<-unique(filter(data,catch_category=="DIS")$species)
cat(List_DIS,sep=", ")
  cat("\n   \n")
  cat("\n   \n") 
```

```{r, echo=FALSE,warning=FALSE,comment="",message=FALSE}
List_sp<-unique(data$species)

#Boxplot of landings weights for each fishing operation: 
weight_species<-data %>% group_by(project,vessel_identifier,trip_code,station_number,gear_label,catch_category,species)%>%
 summarize(weight=sum(weight)*10^(-3))%>%as.data.frame()

weight_species<-as.data.frame(complete(weight_species,nesting(project,vessel_identifier,trip_code,station_number),gear_label,catch_category,species,fill=list(weight=0)))

#One plot by species
List_ggplot<-vector(mode="list",length=length(List_sp))

for(sp in 1:length(List_sp)){
  
  List_ggplot[[sp]]<-ggplot(filter(weight_species,species==List_sp[sp]),aes(y=weight,x=catch_category,fill=gear_label))+
    geom_boxplot()+labs(y = lg[["2_2_catch_labs"]])+ggtitle(List_sp[sp]) +
    stat_summary(fun=mean, geom="point", shape=4, position = position_dodge(0.75),lwd=2)+
    xlab("")+
    theme_light()+
    scale_x_discrete(labels=c(lg[["2_2_DIS"]],lg[["2_2_LAN"]]))+
    #facet_wrap(~species, scales="free") + 
    labs(fill = lg[["0_gear"]])
  print(List_ggplot[[sp]])
}

```


```{r, echo=FALSE,warning=FALSE,comment="",message=FALSE}


##For each species and catch category, paired test (STD/TEST) on the weights difference
#by catch
tab_diff<-weight_species %>%group_by(project,vessel_identifier,trip_code,station_number,catch_category,species)%>%
  summarize(diff_weight=weight[gear_label=="TEST"]-weight[gear_label=="STD"],
            weight_STD=weight[gear_label=="STD"],weight_TEST=weight[gear_label=="TEST"])

test_LAN<-matrix(NA,ncol=6,nrow=length(List_LAN))
row.names(test_LAN)<-List_LAN
test_LAN<-as.data.frame(test_LAN)

for(ii in 1:length(List_LAN)){
  
  #Paired test: (H0): Diff_Poids=0 versus (H1) Diff_Poids not nul, on the mean/median
  #+ Variation rate TEST/STD
  test_LAN[ii,]<-f_test_paired(tab_diff,List_LAN[ii],"LAN")
}
names(test_LAN)<-names(f_test_paired(tab_diff,List_LAN[ii],"LAN"))


test_LAN$moyenne<-round(test_LAN$moyenne,2)
test_LAN$mediane<-round(test_LAN$mediane,2)

test_LAN$moyenne[test_LAN$test=="Fisher"]<-paste(test_LAN$moyenne[test_LAN$test=="Fisher"],"*",sep="")
test_LAN$mediane[test_LAN$test=="Kolmogorov"]<-paste(test_LAN$moyenne[test_LAN$test=="Kolmogorov"],"*",sep="")

test_LAN$pvalue[test_LAN$pvalue< 10^(-2)]<-"< 10-2"
test_LAN$pvalue[test_LAN$pvalue>0.1]<-">0.1"

names(test_LAN)<-c("p-value",lg[["2_2_mean_diff"]],lg[["2_2_median_diff"]],"Test",lg[["2_2_var1"]],lg[["2_2_var2"]])


kable(test_LAN[,-c(4)],digits=2,caption=lg[["2_2_LAN_table_caption"]])


```

*`r lg[["2_2_DIS"]]`*
```{r, echo=FALSE,warning=FALSE,comment="",message=FALSE}

test_DIS<-matrix(NA,ncol=6,nrow=length(List_DIS))
row.names(test_DIS)<-List_DIS
test_DIS<-as.data.frame(test_DIS)

for(ii in 1:length(List_DIS)){
  #Test apparié:  (H0) Diff_Poids=0 versus (H1) Diff_Poids non nulle sur médiane ou moyenne
  #+ Taux de variation TEST/STD
  test_DIS[ii,]<-f_test_paired(tab_diff,List_DIS[ii],"DIS")
}

names(test_DIS)<-names(f_test_paired(tab_diff,List_DIS[ii],"DIS"))

# kable(test_PR[,-4],digits=2,caption="Résultats des tests de différence de biomasses débarquées et rejetées pour chaque espèce. Si la distribution était gaussienne, un test de Fisher sur la moyenne a été effectué, sinon un test de Kolmogorov-Smirnov sur la médiane a été effectué. La statistique testée est identifiée par '*'.")

test_DIS$pvalue[test_DIS$pvalue< 10^(-2)]<-"< 10-2"
test_DIS$pvalue[test_DIS$pvalue>0.1]<-">0.1"

test_DIS$moyenne<-round(test_DIS$moyenne,2)
test_DIS$mediane<-round(test_DIS$mediane,2)

test_DIS$moyenne[which(test_DIS$test=="Fisher")]<-paste(test_DIS$moyenne[which(test_DIS$test=="Fisher")],"*",sep="")
test_DIS$mediane[which(test_DIS$test=="Kolmogorov")]<-paste(test_DIS$moyenne[which(test_DIS$test=="Kolmogorov")],"*",sep="")

names(test_DIS)<-c("p-value",lg[["2_2_mean_diff"]],lg[["2_2_median_diff"]],"Test",lg[["2_2_var1"]],lg[["2_2_var2"]])

kable(test_DIS[,-c(4)],digits=2,caption=lg[["2_2_DIS_table_caption"]])

```



# 3. `r lg[["3_title"]]`

### `r lg[["3_list_size"]]`
```{r, echo=FALSE,warning=FALSE,comment="",message=FALSE}

List_M<-unique(filter(data,is.na(number_at_length)==FALSE)$species)
cat(List_M,sep=", ")

```

### `r lg[["3_size_distribution"]]`

```{r, echo=FALSE,message=FALSE,warning=FALSE,comment="",message=FALSE,fig.width=18,fig.height=6}
  
List_E<-vector(mode="list",length=length(List_M))

for(sp in 1:length(List_M)){
  
  ##Size bounds for plots
  Taille_min<-min(filter(data,species==List_M[sp])$length_class)
  Taille_max<-max(filter(data,species==List_M[sp])$length_class)
   
  #x-Axis title
  unit<-unique(filter(data,species==List_M[sp])$length_code)
  type<-unique(filter(data,species==List_M[sp])$measure_type)
  
  if(type=="CL" | type=="LC"){
   Nom_Taille<-sprintf(lg[["3_CL_labs"]], unit) 
  }
  if(type=="TL" | type=="LT"){
     Nom_Taille<-sprintf(lg[["3_TL_labs"]], unit) 
  }
  
  Taille_com<-filter(min_length,species==List_M[sp])$min_length
  
  #Size counts in the catches
  length_ALL<-filter(data,species==List_M[sp]) %>%
  group_by(gear_label,length_class)%>%
    summarize(n=sum(elevated_number_at_length,na.rm=T))
  
  p1<-ggplot(data=length_ALL, aes(x=length_class, fill=gear_label)) +
      xlim(Taille_min,Taille_max)+
      geom_bar(stat='identity',aes(y=n),position = 'dodge')+
      theme_light()+
    labs(y = lg[["3_n_labs"]],x=Nom_Taille)+
     #facet_wrap(~Fraction, scales="fixed",ncol=3)+ # 1 plot par fraction
      geom_vline(xintercept=Taille_com,color="yellowgreen",size=1,linetype = "dashed")+
    theme(legend.position="bottom",legend.title = element_text(size=22),legend.text = element_text(size=22),axis.text=element_text(size=22),
        axis.title=element_text(size=24),plot.title = element_text(size = 26))+
        labs(fill=lg[["0_gear"]])+
    ylim(c(0,max(length_ALL$n)))+
   #ggtitle(paste0(List_M[sp]," (Total)"))  
    ggtitle("Total")
   
  #print(p1)
  
  #Size counts by catch category
  length_cat<-filter(data,species==List_M[sp]) %>%
  group_by(gear_label,length_class,catch_category)%>%
    summarize(n=sum(elevated_number_at_length,na.rm=T))
  
  p2<-ggplot(data=filter(length_cat,catch_category=="LAN"), aes(x=length_class, fill=gear_label)) +
      xlim(Taille_min,Taille_max)+
      geom_bar(stat='identity',aes(y=n),position = 'dodge')+
      theme_light()+
    labs(y = lg[["3_n_labs"]],x=Nom_Taille)+
      geom_vline(xintercept=Taille_com,color="yellowgreen",size=1,linetype = "dashed")+
          theme(legend.position="bottom",legend.title = element_text(size=22),legend.text = element_text(size=22),axis.text=element_text(size=22),
        axis.title=element_text(size=24),plot.title = element_text(size = 26))+
        labs(fill=lg[["0_gear"]])+
        ylim(c(0,max(length_ALL$n)))+
     #ggtitle(paste0(List_M[sp]," (Débarquements)"))
        ggtitle(lg[["2_2_LAN"]])
  #print(p2)
  
  p3<-ggplot(data=filter(length_cat,catch_category=="DIS"), aes(x=length_class, fill=gear_label)) +
      xlim(Taille_min,Taille_max)+
      geom_bar(stat='identity',aes(y=n),position = 'dodge')+
      theme_light()+
    labs(y = lg[["3_n_labs"]],x=Nom_Taille)+
      geom_vline(xintercept=Taille_com,color="yellowgreen",size=1,linetype = "dashed")+
     theme(legend.position="bottom",legend.title = element_text(size=22),legend.text = element_text(size=22),axis.text=element_text(size=22),
        axis.title=element_text(size=24),plot.title = element_text(size = 26))+
    labs(fill=lg[["0_gear"]])+
        ylim(c(0,max(length_ALL$n)))+
        ggtitle(lg[["2_2_DIS"]])
  #   ggtitle(paste0(List_M[sp]," (Rejets)"))
  #print(p3)
  
  
  p<-ggarrange(p1,p2,p3,nrow=1,common.legend = T)
  
  cat(List_M[sp])

  print(p)

  ##List by species of escapment rates (STD-SEL)/STD: 
  #on the whoel catch and lower/upper min_length.
  
  nSTD<-sum(filter(length_ALL,gear_label=="STD")$n,na.rm=T)
  nSEL<-sum(filter(length_ALL,gear_label=="TEST")$n,na.rm=T)
  taux_Total<-(nSTD-nSEL)/nSTD
  
  nSTD<-sum(filter(length_ALL,gear_label=="STD" & length_class >= Taille_com)$n,na.rm=T)
  nSEL<-sum(filter(length_ALL,gear_label=="TEST" & length_class >= Taille_com)$n,na.rm=T)
  taux_com<-(nSTD-nSEL)/nSTD
  
  nSTD<-sum(filter(length_ALL,gear_label=="STD" & length_class < Taille_com)$n,na.rm=T)
  nSEL<-sum(filter(length_ALL,gear_label=="TEST" & length_class < Taille_com)$n,na.rm=T)
  taux_HT<-(nSTD-nSEL)/nSTD
  
  tab_E<-data.frame(Espece=List_M[sp],taux_Total*100,taux_com*100,taux_HT*100)
  
  List_E[[sp]]<-tab_E

}


Tab_E<-bind_rows(List_E)

names(Tab_E)<-c(lg[["3_species"]],lg[["3_global"]],lg[["3_taille_com"]],lg[["3_undersize"]])

kable(Tab_E,digits=2,caption=lg[["3_escapement"]])

```


### `r lg[["3_selectivity_curve"]]`

```{r, echo=FALSE,warning=FALSE,comment="",message=FALSE,fig.asp=0.7}

for(sp in 1:length(List_M)){
  

  length_sp<-filter(data,species==List_M[sp]) %>% group_by(gear_label,length_class) %>%
  summarize(n=sum(elevated_number_at_length,na.rm=T)) %>%as.data.frame()
  
  #sel relative = TEST/TOTAL
  length_sp<-complete(length_sp,gear_label,length_class,fill=list(n=0))

  Rel_Sel<-length_sp %>% group_by(length_class)%>%
    summarize(rel_sel=n[gear_label=="TEST"]/sum(n),n_STD=sum(n[gear_label=="STD"]),n_TEST=sum(n[gear_label=="TEST"]))%>%as.data.frame()

  taille_com<-filter(min_length,species==List_M[sp])$min_length
  
   #x_title
  unit<-unique(filter(data,species==List_M[sp])$length_code)
  type<-unique(filter(data,species==List_M[sp])$measure_type)

   if(type=="CL" | type=="LC"){
      Nom_Taille<-sprintf(lg[["3_CL_labs"]], unit) 
   }
   if(type=="TL" | type=="LT"){
      Nom_Taille<-sprintf(lg[["3_TL_labs"]], unit) 
   }
  
 p<-ggplot(data=Rel_Sel)+
    geom_point(aes(x=length_class,y=rel_sel,size=n_STD+n_TEST))+
     guides(size=guide_legend(title = "n"))+
    xlab(Nom_Taille)+ylab(lg[["3_rel_selectivity"]])+
   geom_hline(yintercept=0.5, linetype="dashed", color = "grey")+
     geom_vline(xintercept=taille_com,size=1, linetype="dashed", color = "green")+
    ggtitle(List_M[sp])
  
  print(p)
  
}

```
