---
title: "`r lg[['0_main_title']]`"
subtitle: "`r lg[['0p_sub_title_paired']]`"
output: 
  html_document: 
    keep_md: true
    toc: true
    toc_float: true
    number_sections: true
    fig_caption: TRUE
    theme: lumen
params:
  lg: NULL
---

<br/> <br/>


# `r lg[['1_title']]`

## `r lg[['0_title_device']]`


```{r, echo=FALSE,warning=FALSE,comment="",message=FALSE}

## Creation of a table with gear name, selective device, codend mesh size
# and length of the headline


df<-data %>%
  group_by(gear_label) %>%
  summarise(type=unique(gear_type),sel=unique(selective_device),mesh=unique(mesh_gauge_codend_mm),length=unique(headline_cumulative_length)) %>% as.data.frame()

names(df)<-c("",lg[["0_gear"]],lg[["0_selective_device"]],lg[["0_codend_mesh"]],lg[["0_headline"]])
  
kable(df)

```



## `r lg[['1_subtitle_vessel_trip']]`


```{r, echo=FALSE,warning=FALSE,comment="",message=FALSE}

## Creation of a table with vessel name and trip code. 
# For each vessel x trip :number of stations and dates


  df<-data %>%
  group_by(project,vessel_identifier,vessel_name,trip_code) %>%
  summarise(NombreOP=length(unique(station_number)),Debut=unique(departure_date_time),Fin=unique(return_date_time)) %>% as.data.frame()
  
  names(df)<-c(lg[["1_project"]],lg[["1_ID_vessel"]],lg[["1_vessel"]],lg[["1_ID_trip"]],lg[["1_FO"]],lg[["1_start_date"]],lg[["1_end_date"]])
  
kable(df)

```


## `r lg[['1_subtitle_maps']]`

```{r maps, echo=FALSE,warning=FALSE,comment="",message=FALSE,fig.width=30,fig.height=12}

Maps

```

<br/>

## `r lg[['1_subtitle_fishing_conditions']]`

<br/>

```{r fishing_duration, echo=FALSE,warning=FALSE,fig.cap=lg[['1_duration_caption']],comment="",message=FALSE,fig.asp=0.5}

tab_OP<- data %>% group_by(project,vessel_identifier,trip_code,tag_operation,gear_label)%>%
    summarize(fishing_duration=unique(fishing_duration),gear_depth=unique(gear_depth),
              wind_force_beaufort=unique(wind_force_beaufort),gear_speed=unique(gear_speed),
              sea_state=unique(sea_state))

nrow_info<-nrow(tab_OP)

tab_tag<- data %>% 
  group_by(project,vessel_identifier,trip_code,tag_operation)%>%
  summarize(fishing_duration_STD=unique(fishing_duration[gear_label=="STD"]),fishing_duration_TEST=unique(fishing_duration[gear_label=="TEST"]),
            gear_depth_STD=unique(gear_depth[gear_label=="STD"]),gear_depth_TEST=unique(gear_depth[gear_label=="TEST"]),
            wind_force_beaufort_STD=unique(wind_force_beaufort[gear_label=="STD"]),wind_force_beaufort_TEST=unique(wind_force_beaufort[gear_label=="TEST"]),
            gear_speed_STD=unique(gear_speed[gear_label=="STD"]),gear_speed_TEST=unique(gear_speed[gear_label=="TEST"]),
            sea_state_STD=unique(sea_state[gear_label=="STD"]),sea_state_TEST=unique(sea_state[gear_label=="TEST"]))

g_OP<-ggplot(tab_OP,aes(y=fishing_duration,x=gear_label,fill=gear_label))+
  geom_boxplot(width=0.5)+labs(y=lg[["1_duration_labs"]])+
  stat_summary(fun="mean", geom="point", shape=4, lwd=2)+
  #geom_point(aes(x=0,y=mean(fishing_duration)),shape=4) + 
  theme(legend.position = "None",axis.text=element_text(size=8),
        axis.title=element_text(size=10))+
    xlab("")

g_tag<-ggplot(tab_tag)+
  geom_point(aes(x=fishing_duration_STD,y=fishing_duration_TEST))+
  xlab("STD")+ylab("TEST")

if(length(which(is.na(tab_OP$fishing_duration)==FALSE))>0){
ggarrange(g_OP,g_tag)
}

nNA<-length(which(is.na(tab_OP$fishing_duration)==T))
if(nNA>0){cat(sprintf(lg[["1_missing_values"]],nNA,nrow_info))}
```
<br/>

```{r fishing_depth, echo=FALSE,warning=FALSE,fig.cap=lg[['1_depth_caption']],comment="",message=FALSE,fig.asp=0.5}

# g_OP<-ggplot(tab_OP,aes(x=gear_depth,fill=gear_label))+
#   geom_histogram(position="dodge")+labs(y = "Opérations de pêche",x="Profondeur (m)")+
#   theme(legend.position = "top")+#,axis.text=element_text(size=12),axis.title=element_text(size=14))
# labs(fill="Engin")

g_OP<-ggplot(tab_OP,aes(y=gear_depth,x=gear_label,fill=gear_label))+
  geom_boxplot(width=0.5)+labs(y=lg[["1_depth_labs"]])+
  stat_summary(fun="mean", geom="point", shape=4, lwd=2)+
  #geom_point(aes(x=0,y=mean(fishing_duration)),shape=4) + 
  theme(legend.position = "None",axis.text=element_text(size=8),
        axis.title=element_text(size=10))+
    xlab("")

g_tag<-ggplot(tab_tag)+
  geom_point(aes(x=gear_depth_STD,y=gear_depth_TEST))+
  xlab("STD")+ylab("TEST")

if(length(which(is.na(tab_OP$gear_depth)==FALSE))>0){
ggarrange(g_OP,g_tag)
}
nNA<-length(which(is.na(tab_OP$gear_label)==T))
if(nNA>0){cat(sprintf(lg[["1_missing_values"]],nNA,nrow_info))}


```
<br/>

```{r vessel_speed, echo=FALSE,warning=FALSE,fig.cap=lg[['1_speed_caption']],comment="",message=FALSE,fig.asp=0.5}

g_OP<-ggplot(tab_OP,aes(y=gear_speed,x=gear_label,fill=gear_label))+
  geom_boxplot(width=0.5)+labs(y=lg[["1_speed_labs"]])+
  stat_summary(fun="mean", geom="point", shape=4, lwd=2)+
  theme(legend.position = "None",axis.text=element_text(size=8),
        axis.title=element_text(size=10))+
    xlab("")

g_tag<-ggplot(tab_tag)+
  geom_point(aes(x=gear_speed_STD,y=gear_speed_TEST))+
  xlab("STD")+ylab("TEST")

if(length(which(is.na(tab_OP$gear_speed)==FALSE))>0){
ggarrange(g_OP,g_tag)
}

nNA<-length(which(is.na(tab_OP$gear_speed)==T))
if(nNA>0){cat(sprintf(lg[["1_missing_values"]],nNA,nrow_info))}


```
<br/>

```{r wind_force, echo=FALSE,warning=FALSE,fig.cap=lg[['1_wind_caption']],comment="",message=FALSE,fig.asp=0.5}

g_OP<-ggplot(tab_OP,aes(y=wind_force_beaufort,x=gear_label,fill=gear_label))+
  geom_boxplot(width=0.5)+labs(y=lg[["1_wind_labs"]])+
  stat_summary(fun="mean", geom="point", shape=4, lwd=2)+
  theme(legend.position = "None",axis.text=element_text(size=8),
        axis.title=element_text(size=10))+
    xlab("")

g_tag<-ggplot(tab_tag)+
  geom_point(aes(x=wind_force_beaufort_STD,y=wind_force_beaufort_TEST))+
  xlab("STD")+ylab("TEST")

if(length(which(is.na(tab_OP$wind_force_beaufort)==FALSE))>0){
  ggarrange(g_OP,g_tag)
}

nNA<-length(which(is.na(tab_OP$wind_force_beaufort)==T))
if(nNA>0){cat(sprintf(lg[["1_missing_values"]],nNA,nrow_info))}

```

<br/>

```{r sea_state, echo=FALSE,warning=FALSE,fig.cap=lg[['1_sea_state_caption']],comment="",message=FALSE,fig.asp=0.5}

g_OP<-ggplot(tab_OP,aes(y=sea_state,x=gear_label,fill=gear_label))+
  geom_boxplot(width=0.5)+labs(y=lg[["1_sea_state_labs"]])+
  stat_summary(fun="mean", geom="point", shape=4, lwd=2)+
  theme(legend.position = "None",axis.text=element_text(size=8),
        axis.title=element_text(size=10))+
    xlab("")

g_tag<-ggplot(tab_tag)+
  geom_point(aes(x=sea_state_STD,y=sea_state_TEST))+
  xlab("STD")+ylab("TEST")

if(length(which(is.na(tab_OP$sea_state)==FALSE))>0){
  ggarrange(g_OP,g_tag)
}

nNA<-length(which(is.na(tab_OP$sea_state)==T))
if(nNA>0){cat(sprintf(lg[["1_missing_values"]],nNA,nrow_info))}

```
<br/>

```{r seabed, echo=FALSE,warning=FALSE,fig.cap=lg[['1_seabed_caption']],comment="",message=FALSE,fig.asp=0.5}

data$diurnal_operation<-factor(data$diurnal_operation,levels=c("Y","N"),labels=c("Jour","Nuit"))

#Conditions de pêche /OP - variables catégorielles
tab_OP2<- data %>% group_by(project,vessel_identifier,trip_code,tag_operation,gear_label)%>%
    summarize(seabed_features=unique(seabed_features),
              wind_cardinal_direction=unique(wind_cardinal_direction),diurnal_operation=unique(diurnal_operation))
nrow_info2<-nrow(tab_OP2)
tab_tag<- data %>% 
  group_by(project,vessel_identifier,trip_code,tag_operation)%>%
  summarize(seabed_features_STD=unique(seabed_features[gear_label=="STD"]),seabed_features_TEST=unique(seabed_features[gear_label=="TEST"]),
  wind_cardinal_direction_STD=unique(wind_cardinal_direction[gear_label=="STD"]),wind_cardinal_direction_TEST=unique(wind_cardinal_direction[gear_label=="TEST"]),
  diurnal_operation_STD=unique(diurnal_operation[gear_label=="STD"]),diurnal_operation_TEST=unique(diurnal_operation[gear_label=="TEST"]))

g_OP<-ggplot(tab_OP2,aes(x=seabed_features,fill=gear_label))+ 
  geom_bar(stat = 'count',position="dodge") +
 labs(y = lg[["1_FO"]],x=lg[["1_seabed_labs"]])+
  theme(legend.position = "top")+#,axis.text=element_text(size=12),axis.title=element_text(size=14))
labs(fill="Engin")

g_tag<-ggplot(tab_tag)+
  geom_point(aes(x=seabed_features_STD,y=seabed_features_TEST))+
  xlab("STD")+ylab("TEST")

if(length(which(is.na(tab_OP$seabed_features)==FALSE))>0){
ggarrange(g_OP,g_tag)
}

nNA<-length(which(is.na(tab_OP2$seabed_features)==T))
if(nNA>0){cat(sprintf(lg[["1_missing_values"]],nNA,nrow_info2))}

```
<br/>

```{r wind_direction, echo=FALSE,warning=FALSE,fig.cap=lg[['1_wind_dir_caption']],comment="",message=FALSE,fig.asp=0.5}

g_OP<-ggplot(tab_OP2,aes(x=wind_cardinal_direction,fill=gear_label))+ 
  geom_bar(stat = 'count',position="dodge") +
 labs(y = lg[["1_FO"]],x=lg[["1_wind_dir_labs"]])+
   theme(legend.position = "top")+#,axis.text=element_text(size=12),axis.title=element_text(size=14))
labs(fill="Engin")

g_tag<-ggplot(tab_tag)+
  geom_point(aes(x=wind_cardinal_direction_STD,y=wind_cardinal_direction_TEST))+
  xlab("STD")+ylab("TEST")

if(length(which(is.na(tab_OP2$wind_cardinal_direction)==FALSE))>0){
ggarrange(g_OP,g_tag)
}

nNA<-length(which(is.na(tab_OP2$wind_cardinal_direction)==T))
if(nNA>0){cat(sprintf(lg[["1_missing_values"]],nNA,nrow_info2))}

```

<br/>

```{r day_night, echo=FALSE,warning=FALSE,fig.cap=lg[['1_day_caption']],comment="",message=FALSE,fig.asp=0.5}

g_OP<-ggplot(tab_OP2,aes(x=diurnal_operation,fill=gear_label))+ 
  geom_bar(stat = 'count',position="dodge") +
 labs(y = lg[["1_FO"]],x="")+
  theme(legend.position = "top")+#,axis.text=element_text(size=12),axis.title=element_text(size=14))
labs(fill=lg[["0_gear"]])

g_tag<-ggplot(tab_tag)+
  geom_point(aes(x=diurnal_operation_STD,y=diurnal_operation_TEST))+
  xlab("STD")+ylab("TEST")
  
if(length(which(is.na(tab_OP2$diurnal_operation)==FALSE))>0){
ggarrange(g_OP,g_tag)
}

nNA<-length(which(is.na(tab_OP2$diurnal_operation)==T))
if(nNA>0){cat(sprintf(lg[["1_missing_values"]],nNA,nrow_info2))}

```

<br/>
<br/>


<p style="text-align: center;color:blue">**`r lg[['1_subtitle_fishing_summary']]`**</p>



```{r, echo=FALSE,warning=FALSE,comment="",message=FALSE}

## Table of statistics (for continuous variables only)
varC<-c("fishing_duration","gear_depth","gear_speed","wind_force_beaufort","sea_state")

df<-data.frame(Variable=c(lg[["1_duration_labs"]],lg[["1_depth_labs"]],lg[["1_speed_labs"]],lg[["1_wind_labs"]],lg[["1_sea_state_labs"]])) 

df$min<-apply(tab_OP[,varC],2,"min",na.rm=T)
df$max<-apply(tab_OP[,varC],2,"max",na.rm=T)
df$mean<-apply(tab_OP[,varC],2,"mean",na.rm=T)
df$median<-apply(tab_OP[,varC],2,"median",na.rm=T)

df$diff<-data.frame(tab_OP) %>%
  summarize(fishing_duration=mean(fishing_duration[gear_label=="TEST"]-fishing_duration[gear_label=="STD"],na.rm=T),
            gear_depth=mean(gear_depth[gear_label=="TEST"]-gear_depth[gear_label=="STD"],na.rm=T),
            gear_speed=mean(gear_speed[gear_label=="TEST"]-gear_speed[gear_label=="STD"],na.rm=T),
            wind_force_beaufort=mean(wind_force_beaufort[gear_label=="TEST"]-wind_force_beaufort[gear_label=="STD"],na.rm=T),
            sea_state=mean(sea_state[gear_label=="TEST"]-sea_state[gear_label=="STD"],na.rm=T))%>%as.numeric()
  
  
df[,-1]<-round(df[,-1],1)

df$nNA<-apply(tab_OP[,varC],2,function(x){length(which(is.na(x)==TRUE))})

# #For the total catch and sorting time of the catch
# var<-c("catch_weight","sorting_time")
# 
# df2<-data.frame(Variable=c("Poids de la capture (kg)","Durée de tri (min)"))  
# df2$min<-apply(tab_capture[,var],2,"min",na.rm=T)
# df2$max<-apply(tab_capture[,var],2,"max",na.rm=T)
# df2$mean<-apply(tab_capture[,var],2,"mean",na.rm=T)
# df2$median<-apply(tab_capture[,var],2,"median",na.rm=T)
# 
# df2[,-1]<-round(df2[,-1],1)
# df2$nNA<-apply(tab_capture[,var],2,function(x){length(which(is.na(x)==TRUE))})
# 
# df2$diff<-data.frame(tab_capture) %>%
#   summarize(catch_weight=mean(catch_weight[gear_label=="TEST"]-catch_weight[gear_label=="STD"],na.rm=T),
#             sorting_time=mean(sorting_time[gear_label=="TEST"]-sorting_time[gear_label=="STD"],na.rm=T))%>%as.numeric()
# 
# df<-rbind(df,df2)

if(sum(df$nNA>0)){
names(df)<-c("","Min","Max",lg[["1_mean"]],lg[["1_median"]],lg[["1_difference"]],lg[["1_values"]])

kable(df)
}else{df<-select(df,-nNA)
names(df)<-c("","Min","Max",lg[["1_mean"]],lg[["1_median"]],lg[["1_difference"]])
kable(df)
}

```

<br/> <br/>

# `r lg[['2_title']]`

## `r lg[['2_1_subtitle']]`

### `r lg[['2_1_subtitle_catch_weight']]`

```{r total_catch_weight, echo=FALSE,warning=FALSE,fig.cap=lg[['2_1_catch_caption']],comment="",message=FALSE}

#Comparison of catch weight, catch sorting duration and discard weight by pair :

## Calculation of catch sorting duration
data$sorting_start_date_time<-as.POSIXct(data$sorting_start_date_time,format="%Y-%m-%d %H:%M:%S")
data$sorting_end_date_time<-as.POSIXct(data$sorting_end_date_time,format="%Y-%m-%d %H:%M:%S")
data$sorting_time<-with(data,difftime(sorting_end_date_time,sorting_start_date_time,units="mins"))
data<-data|> mutate(landing_weight=catch_weight-discard_weight)

#By catch
tab_capture<- data %>% 
  group_by(project,vessel_identifier,trip_code,tag_operation,gear_label)%>%
  summarize(catch_weight=unique(catch_weight),sorting_time=unique(sorting_time),
              discard_weight=unique(discard_weight),landing_weight=unique(landing_weight))

nrow_info<- nrow(tab_capture)

#By pair
tab_tag<- data %>% 
  group_by(project,vessel_identifier,trip_code,tag_operation)%>%
  summarize(catch_weight_STD=unique(catch_weight[gear_label=="STD"]),catch_weight_TEST=unique(catch_weight[gear_label=="TEST"]),
            sorting_time_STD=unique(sorting_time[gear_label=="STD"]),sorting_time_TEST=unique(sorting_time[gear_label=="TEST"]),
            discard_weight_STD=unique(discard_weight[gear_label=="STD"]),discard_weight_TEST=unique(discard_weight[gear_label=="TEST"]),
              landing_weight_STD=unique(landing_weight[gear_label=="STD"]),landing_weight_TEST=unique(landing_weight[gear_label=="TEST"]))

if(length(which(is.na(tab_capture$catch_weight)==FALSE))>0){
  
  g_OP<-ggplot(tab_capture,aes(y=catch_weight,x=gear_label))+
    theme_light()+
  geom_boxplot(width=0.5,aes(fill=gear_label))+labs(y=lg[["2_1_catch_labs"]])+
    
   stat_summary(fun="mean", geom="point", shape=4, position = position_dodge(0.75),lwd=2)+
  theme(legend.position = "None",axis.text=element_text(size=8),
        axis.title=element_text(size=10))+
    xlab("")
  
  g_tag<-ggplot(tab_tag)+
      theme_light()+
    geom_point(aes(x=catch_weight_STD,y=catch_weight_TEST))+
    xlab("STD")+ylab("TEST")
  
  ggarrange(g_OP,g_tag)
}

nNA<-length(which(is.na(tab_capture$catch_weight)==T))
if(nNA>0){cat(sprintf(lg[["1_missing_values"]],nNA,nrow_info))}

```


### `r lg[["2_1_subtitle_sorting"]]`

```{r sorting_time, echo=FALSE,warning=FALSE,fig.cap=lg[['2_1_sorting_caption']],comment="",message=FALSE,fig.asp=0.5}

if(length(which(is.na(tab_capture$sorting_time)==FALSE))>0){
 
  g_OP<-ggplot(tab_capture,aes(y=sorting_time,x=gear_label))+
        theme_light()+
  geom_boxplot(width=0.5,aes(fill=gear_label))+labs(y=lg[["2_1_sorting_labs"]])+
   stat_summary(fun="mean", geom="point", shape=4, position = position_dodge(0.75),lwd=2)+
  theme(legend.position = "None",axis.text=element_text(size=8),
        axis.title=element_text(size=10))+
    xlab("")
  
  g_tag<-ggplot(tab_tag)+
       theme_light()+
    xlab("STD")+ylab("TEST")+
    geom_point(aes(x=sorting_time_STD,y=sorting_time_TEST))
  
  ggarrange(g_OP,g_tag)
}

nNA<-length(which(is.na(tab_capture$sorting_time)==T))
if(nNA>0){cat(sprintf(lg[["1_missing_values"]],nNA,nrow_info))}

```



```{r, echo=FALSE,warning=FALSE,comment="",message=FALSE}

# Difference of biomass between TEST and STD for each fishing operation and fraction:

tab_diff<-tab_capture %>% 
  group_by(project,vessel_identifier,trip_code,tag_operation)%>%
  summarize(weight_DIS_STD=sorting_time[gear_label=="STD"],weight_DIS_TEST=sorting_time[gear_label=="TEST"],
            diff_DIS=sorting_time[gear_label=="TEST"]-sorting_time[gear_label=="STD"])

diff_DIS<-tab_diff$diff_DIS

#Normality Shapiro-Wilk test
#Encapsulation of errors: 

test1<-tryCatch(shapiro.test(diff_DIS), error = function(e){"e"})

#if no "error":
if(class(test1) =="htest"){
  
  #If normality hypothesis is not rejected (ie. p-value from Shapiro test >0.05), Student test:
  if(test1$p.value > 0.05){
    test2<-tryCatch(t.test(x=diff_DIS,mu=0) , error = function(e){"e"})
  }
  #If normality hypothesis is rejected (ie. p-value from Shapiro test <0.05), Mann-Whitney/Wilcoxon test:
  if(test1$p.value <= 0.05){
    test2<-tryCatch(wilcox.test(diff_DIS, paired =F, correct = T, exact = F), error = function(e){"e"})
  }
  
  if(class(test2) == "htest"){#if no error
    
    if(test2$p.value<=0.05){
      
      cat(lg[["2_1_sorting_test_diff"]],"\n")
 }else{ cat(lg[["2_1_sorting_test_nodiff"]],"\n")}
      
  }    
      
  if(test1$p.value <= 0.05){
     med<-  abs(round(median(diff_DIS),3))
    sign<-c(lg[["2_1_less"]],lg[["2_1_more"]])[as.numeric(eval(median(diff_DIS)>0))+1]
    
        cat(sprintf(lg[["2_1_sorting_test_med"]],med,sign,pvalue) ) 
      }
  
  if(test1$p.value > 0.05){
     mean<-  abs(round(mean(diff_DIS),3))
    sign<-c(lg[["2_1_less"]],lg[["2_1_more"]])[as.numeric(eval(mean(diff_DIS)>0))+1]
    
       cat(sprintf(lg[["2_1_sorting_test_mean"]],med,sign,pvalue) )  
      }
   
}


```


```{r, echo=FALSE,warning=FALSE,comment="",message=FALSE}

#Variation rate (TEST-STD)/STD
Tot_TEST<-sum(tab_diff$weight_DIS_TEST)
Tot_STD<-sum(tab_diff$weight_DIS_STD)

Var_Rate<-(Tot_TEST-Tot_STD)/Tot_STD*100

if(is.na(Var_Rate)==FALSE){
  sign<-c(lg[["2_1_decrease"]] ,lg[["2_1_increase"]])[as.numeric(eval(Var_Rate>0))+1]
  rate<-abs(round(Var_Rate,2))
cat(sprintf(lg[["2_1_sorting_var1"]],sign,rate))

Var_Rate2<-with(tab_diff,mean(diff_DIS/weight_DIS_STD))*100
  
   rate<-abs(round(Var_Rate2,2))
   
cat(paste0(lg[['2_1_subtitle_sorting_variation']]," : \n"))

cat(sprintf(lg[["2_1_sorting_var2"]],sign,rate))
}

```



### `r lg[['2_1_subtitle_frac_weight']]`


<br/>

```{r fraction_weights, echo=FALSE,warning=FALSE,fig.cap="Poids total des rejets par opération de pêche.",message=FALSE,fig.width=5}

if(length(which(is.na(tab_capture$discard_weight)==FALSE))>0){
 gg_LAN<-ggplot(tab_capture,aes(y=landing_weight,x=gear_label,fill=gear_label))+
  geom_boxplot(width=0.5)+labs(y = lg[["2_1_landing_weight_labs"]])+
  xlab(lg[["0_gear"]])+
       theme_light()+
    theme(legend.position = "None",axis.text=element_text(size=8),
        axis.title=element_text(size=10))+
  stat_summary(fun="mean", geom="point", shape=4, position = position_dodge(0.75),lwd=2)
 
   gg_DIS<-ggplot(tab_capture,aes(y=discard_weight,x=gear_label,fill=gear_label))+
  geom_boxplot(width=0.5)+labs(y = lg[["2_1_discard_weight_labs"]])+
  xlab(lg[["0_gear"]])+
       theme_light()+
    theme(legend.position = "None",axis.text=element_text(size=8),
        axis.title=element_text(size=14))+
  stat_summary(fun="mean", geom="point", shape=4, position = position_dodge(0.75),lwd=2)
 
 
   ggarrange(gg_LAN,gg_DIS)
}

```
<br/>

**`r lg[['2_1_subtitle_discard_variation']]`**

```{r, echo=FALSE,warning=FALSE,comment="",message=FALSE}

#For each pair, difference of discards weights TEST-STD:
diff_DIS<-with(tab_tag,discard_weight_TEST-discard_weight_STD)

#Test de Shapiro-Wilk for normality

test1<-tryCatch(shapiro.test(diff_DIS), error = function(e){"e"})

#if no "error":
if(class(test1) =="htest"){
  
  #If normality not rejected (p-value >0.05), Student test:
  if(test1$p.value > 0.05){
    test2<-tryCatch(t.test(x=diff_DIS,mu=0) , error = function(e){"e"})
  }
   #If normality rejected (p-value <= 0.05), Mann-Whitney/Wilcoxon test:
  if(test1$p.value <= 0.05){
    test2<-tryCatch(wilcox.test(diff_DIS, paired =F, correct = T, exact = F), error = function(e){"e"})
  }
  
  if(class(test2) == "htest"){#if no error
    
    if(test2$p.value<=0.05){
        cat(lg[["2_1_discard_test_diff"]],"\n")
 }else{ cat(lg[["2_1_discard_test_nodiff"]],"\n")}
  }    
      
  if(test1$p.value <= 0.05){
    med<-abs(round(median(diff_DIS),3))
    sign<-c(lg[["2_1_less"]],lg[["2_1_more"]])[as.numeric(eval(median(diff_DIS)>0))+1]
    pvalue<-round(test2$p.value,4)
    cat(sprintf(lg[["2_1_discard_test_med"]],med,sign,pvalue))
      }
  
  if(test1$p.value > 0.05){
       mean<-abs(round(mean(diff_DIS),3))
    sign<-c(lg[["2_1_less"]],lg[["2_1_more"]])[as.numeric(eval(mean(diff_DIS)>0))+1]
    pvalue<-round(test2$p.value,4)
    cat(sprintf(lg[["2_1_discard_test_mean"]],mean,sign,pvalue))
  }
  
 
   
}

```

```{r, echo=FALSE,warning=FALSE,comment="",message=FALSE}

#Variation rate (TEST-STD)/STD
Tot_TEST<-sum(tab_tag$discard_weight_TEST)
Tot_STD<-sum(tab_tag$discard_weight_STD)

Var_Rate<-(Tot_TEST-Tot_STD)/Tot_STD*100
  
sign<-c(lg[["2_1_decrease"]] ,lg[["2_1_increase"]])[as.numeric(eval(Var_Rate>0))+1]
rate<-abs(round(Var_Rate,2))
cat(sprintf(lg[["2_1_discard_var1"]],sign,rate))

Var_Rate2<-with(tab_tag,(discard_weight_TEST-discard_weight_STD)/discard_weight_STD)*100
  
sign<-c(lg[["2_1_decrease"]] ,lg[["2_1_increase"]])[as.numeric(eval(mean(Var_Rate2)>0))+1]
rate<-abs(round(mean(Var_Rate2),2))
cat(sprintf(lg[["2_1_discard_var2"]],sign,rate))

```


<br/>

**`r lg[['2_1_subtitle_landing_variation']]`**


```{r, echo=FALSE,warning=FALSE,comment="",message=FALSE}

#For each pair, difference of discards weights TEST-STD:
diff_LAN<-with(tab_tag,landing_weight_TEST-landing_weight_STD)

#Test de Shapiro-Wilk for normality

test1<-tryCatch(shapiro.test(diff_LAN), error = function(e){"e"})

#if no "error":
if(class(test1) =="htest"){
  
  #If normality not rejected (p-value >0.05), Student test:
  if(test1$p.value > 0.05){
    test2<-tryCatch(t.test(x=diff_LAN,mu=0) , error = function(e){"e"})
  }
   #If normality rejected (p-value <= 0.05), Mann-Whitney/Wilcoxon test:
  if(test1$p.value <= 0.05){
    test2<-tryCatch(wilcox.test(diff_LAN, paired =F, correct = T, exact = F), error = function(e){"e"})
  }
  
  if(class(test2) == "htest"){#if no error
    
    if(test2$p.value<=0.05){
        cat(lg[["2_1_landing_test_diff"]],"\n")
 }else{ cat(lg[["2_1_landing_test_nodiff"]],"\n")}
  }    
      
  if(test1$p.value <= 0.05){
    med<-abs(round(median(diff_LAN),3))
    sign<-c(lg[["2_1_less"]],lg[["2_1_more"]])[as.numeric(eval(median(diff_LAN)>0))+1]
    pvalue<-round(test2$p.value,4)
    cat(sprintf(lg[["2_1_landing_test_med"]],med,sign,pvalue))
      }
  
  if(test1$p.value > 0.05){
       mean<-abs(round(mean(diff_LAN),3))
    sign<-c(lg[["2_1_less"]],lg[["2_1_more"]])[as.numeric(eval(mean(diff_LAN)>0))+1]
    pvalue<-round(test2$p.value,4)
    cat(sprintf(lg[["2_1_landing_test_mean"]],mean,sign,pvalue))
  }
  
 
   
}

```


```{r, echo=FALSE,warning=FALSE,comment="",message=FALSE}

#Variation rate (TEST-STD)/STD
Tot_TEST<-sum(tab_tag$landing_weight_TEST)
Tot_STD<-sum(tab_tag$landing_weight_STD)

Var_Rate<-(Tot_TEST-Tot_STD)/Tot_STD*100
  
sign<-c(lg[["2_1_decrease"]] ,lg[["2_1_increase"]])[as.numeric(eval(Var_Rate>0))+1]
rate<-abs(round(Var_Rate,2))
if(is.na(rate)==FALSE){
cat(sprintf(lg[["2_1_discard_var1"]],sign,rate))
}
Var_Rate2<-with(tab_tag,(discard_weight_TEST-discard_weight_STD)/discard_weight_STD)*100
  
sign<-c(lg[["2_1_decrease"]] ,lg[["2_1_increase"]])[as.numeric(eval(mean(Var_Rate2)>0))+1]
rate<-abs(round(mean(Var_Rate2),2))
if(is.na(rate)==FALSE){
cat(sprintf(lg[["2_1_discard_var2"]],sign,rate))
}
```


<br/>

## `r lg[["2_2_subtitle"]]`


```{r, echo=FALSE,warning=FALSE,comment="",message=FALSE}
List_LAN<-unique(filter(data,catch_category=="LAN")$species)
#cat(List_LAN,sep=", ")
List_DIS<-unique(filter(data,catch_category=="DIS")$species)
#cat(List_DIS,sep=", ")

List_sp<-unique(List_LAN,List_DIS)
```
**`r lg[["2_2_list_species"]]`**

`r List_sp`

<br/>

```{r fraction_species_weights, echo=FALSE,warning=FALSE,comment="",message=FALSE}


#Remove lines with NA value in gear_label/catch_category/species (no species observed from a gear of a given station)
data<-filter(data,is.na(gear_label)==FALSE & is.na(catch_category)==FALSE & is.na(species)==FALSE)

#Boxplot of weights by fishing operation for each catch category and gear: 
weight_species<-data |>
  group_by(project,vessel_identifier,trip_code,tag_operation,station_number,gear_label,catch_category,species,
           landing_category,commercial_size_category,subsampling_category,sex)|>
 summarize(weight=unique(weight))|>
  as.data.frame()

weight_species <- weight_species %>% 
 group_by(project,vessel_identifier,trip_code,tag_operation,gear_label,catch_category,species)%>%
 summarize(weight=sum(weight)*10^(-3))%>%
  as.data.frame()

weight_species<-as.data.frame(complete(weight_species,nesting(project,vessel_identifier,trip_code,tag_operation),gear_label,catch_category,species,fill=list(weight=0)))

#One plot by species
List_ggplot<-vector(mode="list",length=length(List_sp))

for(sp in 1:length(List_sp)){
  
  List_ggplot[[sp]]<-ggplot(filter(weight_species,species==List_sp[sp]),aes(y=weight,x=catch_category,fill=gear_label))+
    geom_boxplot()+labs(y = lg[["2_2_catch_labs"]])+ggtitle(List_sp[sp]) +
    stat_summary(fun="mean", geom="point", shape=4, position = position_dodge(0.75),lwd=2)+
    xlab("")+
       theme_light()+
    scale_x_discrete(labels=c(lg[["2_2_DIS"]],lg[["2_2_LAN"]]))+
    labs(fill = lg[["0_gear"]])
  print(List_ggplot[[sp]])
}

```


```{r, echo=FALSE,warning=FALSE,comment="",message=FALSE}

##For each species and fraction, paired test (STD/TEST) on the weights differences by catch
tab_diff<-weight_species %>% group_by(project,vessel_identifier,trip_code,tag_operation,catch_category,species)%>%
  summarize(diff_weight=weight[gear_label=="TEST"]-weight[gear_label=="STD"],
            weight_STD=weight[gear_label=="STD"],weight_TEST=weight[gear_label=="TEST"])

test_LAN<-matrix(NA,ncol=6,nrow=length(List_LAN))
row.names(test_LAN)<-List_LAN
test_LAN<-as.data.frame(test_LAN)

for(ii in 1:length(List_LAN)){
  
  #Paired test:  (H0) Diff_Poids=0 versus (H1) Diff_Poids not nul, for the median or mean
  #+ Variation rate TEST/STD
  test_LAN[ii,]<-f_test_paired( tab_diff, List_LAN[ii],"LAN")
}

names(test_LAN)<-names(f_test_paired(tab_diff,List_LAN[ii],"LAN"))

test_LAN$moyenne<-round(test_LAN$moyenne,2)
test_LAN$mediane<-round(test_LAN$mediane,2)

if("Fisher" %in% test_LAN$test){
test_LAN$moyenne[which(test_LAN$test=="Fisher")]<-paste(test_LAN$moyenne[which(test_LAN$test=="Fisher")],"*",sep="")
}
if("Kolmogorov" %in% test_LAN$test){
test_LAN$mediane[which(test_LAN$test=="Kolmogorov")]<-paste(test_LAN$mediane[which(test_LAN$test=="Kolmogorov")],"*",sep="")
}

test_LAN$pvalue[test_LAN$pvalue< 10^(-2)]<-"< 10-2"
test_LAN$pvalue[test_LAN$pvalue>0.1]<-">0.1"

names(test_LAN)<-c("p-value",lg[["2_2_mean_diff"]],lg[["2_2_median_diff"]],"Test",lg[["2_2_var1"]],lg[["2_2_var2"]])

kable(test_LAN[,-c(4)],digits=2,caption=lg[["2_2_LAN_table_caption"]])

```

<br/>

```{r, echo=FALSE,warning=FALSE,comment="",message=FALSE}

test_DIS<-matrix(NA,ncol=6,nrow=length(List_DIS))
row.names(test_DIS)<-List_DIS
test_DIS<-as.data.frame(test_DIS)

for(ii in 1:length(List_DIS)){
#Paired test :  (H0) Diff_Poids=0 versus (H1) Diff_Poids not nul in mean/median
  #+ Variation rate TEST/STD
  test_DIS[ii,]<-f_test_paired(tab_diff,List_DIS[ii],"DIS")
}

names(test_DIS)<-names(f_test_paired(tab_diff,List_DIS[ii],"LAN"))

test_DIS$pvalue[test_DIS$pvalue< 10^(-2)]<-"< 10-2"
test_DIS$pvalue[test_DIS$pvalue>0.1]<-">0.1"

test_DIS$moyenne<-round(test_DIS$moyenne,2)
test_DIS$mediane<-round(test_DIS$mediane,2)


if("Fisher" %in% test_DIS$test){
test_DIS$moyenne[which(test_DIS$test=="Fisher")]<-paste(test_DIS$moyenne[which(test_DIS$test=="Fisher")],"*",sep="")
}
if("Kolmogorov" %in% test_DIS$test){
test_DIS$mediane[which(test_DIS$test=="Kolmogorov")]<-paste(test_DIS$mediane[which(test_DIS$test=="Kolmogorov")],"*",sep="")
}


names(test_DIS)<-c("p-value",lg[["2_2_mean_diff"]],lg[["2_2_median_diff"]],"Test",lg[["2_2_var1"]],lg[["2_2_var2"]])

kable(test_DIS[,-c(4)],digits=2,caption=lg[["2_2_DIS_table_caption"]])


```

<br/>

# `r lg[["3_title"]]`

**`r lg[["3_list_size"]]`**

```{r, echo=FALSE,warning=FALSE,comment="",message=FALSE}

List_M<-unique(filter(data,is.na(number_at_length)==FALSE)$species)

```

`r List_M`

<br/>

## `r lg[["3_size_distribution"]]`

```{r size_distribution_species, echo=FALSE,message=FALSE,warning=FALSE,comment="",message=FALSE,fig.width=18,fig.height=6}

#Remove lines with NA value in length_class (no species observed from a gear of a given station)
data<-filter(data,is.na(length_class)==FALSE)

if(class(min_length)=="NULL"){
    min_length<-data.frame(min_length=NA,species=List_M)
}

List_E<-vector(mode="list",length=length(List_M))

for(sp in 1:length(List_M)){
  
 #Size bounds for plots
  Taille_min<-min(filter(data,species==List_M[sp])$length_class)
  Taille_max<-max(filter(data,species==List_M[sp])$length_class)
   
 #x-Axis title
 unit<-unique(filter(data,species==List_M[sp])$length_code)
 type<-unique(filter(data,species==List_M[sp])$measure_type)
 
 if(length(unit)>1 | length(unit)>1 ) {
    stop(
      paste("more than one unit or length code for ",List_M[sp]) 
    )
  }  
 
  if(type=="CL" | type=="LC"){
   Nom_Taille<-sprintf(lg[["3_CL_labs"]], unit) 
  }
  if(type=="TL" | type=="LT"){
     Nom_Taille<-sprintf(lg[["3_TL_labs"]], unit) 
  }
 
  Taille_com<-as.numeric(filter(min_length,species==List_M[sp])$min_length)

  #Size counts in the catches
  length_ALL<-filter(data,species==List_M[sp]) %>%
  group_by(gear_label,length_class)%>%
    summarize(n=sum(elevated_number_at_length,na.rm=T))
  
  Name_sp<-List_M[sp]
     
  p1<-ggplot(data=length_ALL, aes(x=length_class, fill=gear_label)) +
      xlim(Taille_min,Taille_max)+
      geom_bar(stat='identity',aes(y=n),position = 'dodge')+
      theme_light()+
    labs(y = lg[["3_n_labs"]],x=Nom_Taille)+
     #facet_wrap(~Fraction, scales="fixed",ncol=3)+ # 1 plot par fraction
      geom_vline(xintercept=Taille_com,color="yellowgreen",size=1,linetype = "dashed")+
    theme(legend.position="bottom",legend.title = element_text(size=22),legend.text = element_text(size=22),axis.text=element_text(size=22),
        axis.title=element_text(size=24),plot.title = element_text(size = 26))+
        labs(fill=lg[["0_gear"]])+
    ylim(c(0,max(length_ALL$n)))+
   #ggtitle(paste0(List_M[sp]," (Total)"))  
    ggtitle(lg[["3_whole"]])
  #print(p)
  
  #Effectifs en taille par fraction
  length_cat<-filter(data,species==List_M[sp]) %>%
  group_by(gear_label,length_class,catch_category)%>%
    summarize(n=sum(elevated_number_at_length,na.rm=T))
  
  p2<-ggplot(data=filter(length_cat,catch_category=="LAN"), aes(x=length_class, fill=gear_label)) +
      xlim(Taille_min,Taille_max)+
      geom_bar(stat='identity',aes(y=n),position = 'dodge')+
      theme_light()+
    labs(y = lg[["3_n_labs"]],x=Nom_Taille)+
      geom_vline(xintercept=Taille_com,color="yellowgreen",size=1,linetype = "dashed")+
          theme(legend.position="bottom",legend.title = element_text(size=22),legend.text = element_text(size=22),axis.text=element_text(size=22),
        axis.title=element_text(size=24),plot.title = element_text(size = 26))+
        labs(fill=lg[["0_gear"]])+
        ylim(c(0,max(length_ALL$n)))+
     #ggtitle(paste0(List_M[sp]," (Débarquements)"))
        ggtitle(lg[["2_2_LAN"]])
  #print(p2)
  
  p3<-ggplot(data=filter(length_cat,catch_category=="DIS"), aes(x=length_class, fill=gear_label)) +
      xlim(Taille_min,Taille_max)+
      geom_bar(stat='identity',aes(y=n),position = 'dodge')+
      theme_light()+
    labs(y = lg[["3_n_labs"]],x=Nom_Taille)+
      geom_vline(xintercept=Taille_com,color="yellowgreen",size=1,linetype = "dashed")+
     theme(legend.position="bottom",legend.title = element_text(size=22),legend.text = element_text(size=22),axis.text=element_text(size=22),
        axis.title=element_text(size=24),plot.title = element_text(size = 26))+
    labs(fill=lg[["0_gear"]])+
        ylim(c(0,max(length_ALL$n)))+
        ggtitle(lg[["2_2_DIS"]])
  #   ggtitle(paste0(List_M[sp]," (Rejets)"))
  #print(p3)
  
  p<-ggarrange(p1,p2,p3,nrow=1,common.legend = T)
  
  cat(List_M[sp])

  print(p)
  
   ##List by species of escapment rates (STD-SEL)/STD: 
  #on the whole catch and lower/upper min_length.
  
  nSTD<-sum(filter(length_ALL,gear_label=="STD")$n,na.rm=T)
  nSEL<-sum(filter(length_ALL,gear_label=="TEST")$n,na.rm=T)
  taux_Total<-(nSTD-nSEL)/nSTD
  
  nSTD<-sum(filter(length_ALL,gear_label=="STD" & length_class >= Taille_com)$n,na.rm=T)
  nSEL<-sum(filter(length_ALL,gear_label=="TEST" & length_class >= Taille_com)$n,na.rm=T)
  taux_com<-(nSTD-nSEL)/nSTD
  
  nSTD<-sum(filter(length_ALL,gear_label=="STD" & length_class < Taille_com)$n,na.rm=T)
  nSEL<-sum(filter(length_ALL,gear_label=="TEST" & length_class < Taille_com)$n,na.rm=T)
  taux_HT<-(nSTD-nSEL)/nSTD
  
  tab_E<-data.frame(Espece=List_M[sp],taux_Total*100,taux_com*100,taux_HT*100)
  
  List_E[[sp]]<-tab_E

}


Tab_E<-bind_rows(List_E)

names(Tab_E)<-c(lg[["3_species"]],lg[["3_global"]],lg[["3_taille_com"]],lg[["3_undersize"]])

kable(Tab_E,digits=2,caption=lg[["3_escapement"]])

```



## `r lg[["3_selectivity_curve"]]`

```{r relative_size_selectivity_species, echo=FALSE,warning=FALSE,comment="",message=FALSE,fig.asp=0.7}

for(sp in 1:length(List_M)){
  

  length_sp<-filter(data,species==List_M[sp]) %>% group_by(gear_label,length_class) %>%
  summarize(n=sum(elevated_number_at_length,na.rm=T)) %>%as.data.frame()
  
  #sel relative = TEST/TOTAL
  length_sp<-complete(length_sp,gear_label,length_class,fill=list(n=0))

  Rel_Sel<-length_sp %>% group_by(length_class)%>%
    summarize(rel_sel=n[gear_label=="TEST"]/sum(n),n_STD=sum(n[gear_label=="STD"]),n_TEST=sum(n[gear_label=="TEST"]))%>%as.data.frame()

  taille_com<-as.numeric(filter(min_length,species==List_M[sp])$min_length)
    
 #Titre en abscisse
 unit<-unique(filter(data,species==List_M[sp])$length_code)
 type<-unique(filter(data,species==List_M[sp])$measure_type)

   if(type=="CL" | type=="LC"){
      Nom_Taille<-sprintf(lg[["3_CL_labs"]], unit) 
   }
   if(type=="TL" | type=="LT"){
      Nom_Taille<-sprintf(lg[["3_TL_labs"]], unit) 
   }
 
  p<-ggplot(data=Rel_Sel)+
    geom_point(aes(x=length_class,y=rel_sel,size=n_STD+n_TEST))+
    guides(size=guide_legend(title = "n"))+
       theme_light()+
    xlab(Nom_Taille)+ylab(lg[["3_rel_selectivity"]])+
   geom_hline(yintercept=0.5, linetype="dashed", color = "grey")+
     geom_vline(xintercept=taille_com,size=1, linetype="dashed", color = "green")+
    ggtitle(List_M[sp])
  
  print(p)
  
}

```
