---
title: "`r lg[['0_main_title']]`"
subtitle: "`r lg[['0u_sub_title_unpaired']]`"
output: word_document
params:
  lg: NULL
---

# `r lg[['0_title_device']]`

```{r, echo=FALSE,warning=FALSE,comment="",message=FALSE}

##Create a table with gear names, selective device, codend mesh size, 
#headline length

df<-data %>%
  group_by(gear_label) %>%
  summarise(type=unique(gear_type),sel=unique(selective_device),mesh=unique(mesh_gauge_codend_mm),length=unique(headline_cumulative_length)) %>% as.data.frame()

names(df)<-c("",lg[["0_gear"]],lg[["0_selective_device"]],lg[["0_codend_mesh"]],lg[["0_headline"]])
  
kable(df)

```


# 1.`r lg[['1_title']]`

### `r lg[['1_subtitle_vessel_trip']]`

```{r, echo=FALSE,warning=FALSE,comment="",message=FALSE}

##Create a table with vessels and trips names for each vesselxtrip: 
#station's numbers, dates
df<-data %>%
  group_by(project,vessel_identifier,vessel_name,trip_code) %>%
  summarise(NombreOP=length(unique(station_number)),Debut=unique(departure_date_time),Fin=unique(return_date_time)) %>% as.data.frame()
  

names(df)<-c(lg[["1_project"]],lg[["1_ID_vessel"]],lg[["1_vessel"]],lg[["1_ID_trip"]],lg[["1_FO"]],lg[["1_start_date"]],lg[["1_end_date"]])

kable(df)

```


### `r lg[['1_subtitle_maps']]`
```{r, echo=FALSE,warning=FALSE,comment="",message=FALSE,fig.width=30,fig.height=12}

Maps

```

### `r lg[['1_subtitle_fishing_conditions']]`


```{r, echo=FALSE,warning=FALSE,fig.cap=lg[['1_duration_caption']],comment="",message=FALSE,fig.asp=0.5}

tab_OP<- data %>% group_by(project,vessel_identifier,trip_code,station_number,gear_label)%>%
    summarize(fishing_duration=unique(fishing_duration),gear_depth=unique(gear_depth),
              wind_force_beaufort=unique(wind_force_beaufort),gear_speed=unique(gear_speed),
              sea_state=unique(sea_state))

nrow_info<-nrow(tab_OP)

if(length(which(is.na(tab_OP$fishing_duration)==FALSE))>0){
  
  ggplot(tab_OP,aes(y=fishing_duration,x=gear_label,fill=gear_label))+
  geom_boxplot(width=0.5)+labs(y=lg[["1_duration_labs"]])+
        theme_light()+
  stat_summary(fun="mean", geom="point", shape=4, lwd=2)+
  #geom_point(aes(x=0,y=mean(fishing_duration)),shape=4) + 
  theme(legend.position = "None",axis.text=element_text(size=8),
        axis.title=element_text(size=10))+
    xlab("")
}

nNA<-length(which(is.na(tab_OP$fishing_duration)==T))
if(nNA>0){cat(sprintf(lg[["1_missing_values"]],nNA,nrow_info))}
  
```


```{r, echo=FALSE,warning=FALSE,fig.cap=lg[['1_depth_caption']],comment="",message=FALSE,fig.asp=0.5}

if(length(which(is.na(tab_OP$gear_depth)==FALSE))>0){
 
    ggplot(tab_OP,aes(y=gear_depth,x=gear_label,fill=gear_label))+
        theme_light()+
  geom_boxplot(width=0.4)+labs(y=lg[["1_depth_labs"]])+
  stat_summary(fun="mean", geom="point", shape=4, lwd=2)+
  theme(legend.position = "None",axis.text=element_text(size=8),
        axis.title=element_text(size=10))+
    xlab("")
}

nNA<-length(which(is.na(tab_OP$gear_label)==T))
if(nNA>0){cat(sprintf(lg[["1_missing_values"]],nNA,nrow_info))}

```


```{r, echo=FALSE,warning=FALSE,fig.cap=lg[['1_speed_caption']],comment="",message=FALSE,fig.asp=0.5}

if(length(which(is.na(tab_OP$gear_speed)==FALSE))>0){
  
   ggplot(tab_OP,aes(y=gear_speed,x=gear_label,fill=gear_label))+
  geom_boxplot(width=0.5)+labs(y=lg[["1_speed_labs"]])+
          theme_light()+
  stat_summary(fun="mean", geom="point", shape=4, lwd=2)+
  theme(legend.position = "None",axis.text=element_text(size=8),
        axis.title=element_text(size=10))+
    xlab("")
}

nNA<-length(which(is.na(tab_OP$gear_speed)==T))
if(nNA>0){cat(sprintf(lg[["1_missing_values"]],nNA,nrow_info))}

```


```{r, echo=FALSE,warning=FALSE,fig.cap=lg[['1_wind_caption']],comment="",message=FALSE,fig.asp=0.5}

if(length(which(is.na(tab_OP$wind_force_beaufort)==FALSE))>0){
     ggplot(tab_OP,aes(y=wind_force_beaufort,x=gear_label,fill=gear_label))+
          theme_light()+
  geom_boxplot(width=0.4)+labs(y=lg[["1_wind_labs"]])+
  stat_summary(fun="mean", geom="point", shape=4, lwd=2)+
  theme(legend.position = "None",axis.text=element_text(size=8),
        axis.title=element_text(size=10))+
    xlab("")
}

nNA<-length(which(is.na(tab_OP$wind_force_beaufort)==T))
if(nNA>0){cat(sprintf(lg[["1_missing_values"]],nNA,nrow_info))}

```

```{r, echo=FALSE,warning=FALSE,fig.cap=lg[['1_sea_state_caption']],comment="",message=FALSE,fig.asp=0.5}

if(length(which(is.na(tab_OP$sea_state)==FALSE))>0){
     ggplot(tab_OP,aes(y=sea_state,x=gear_label,fill=gear_label))+
          theme_light()+
  geom_boxplot(width=0.4)+labs(y=lg[["1_sea_state_labs"]])+
  stat_summary(fun="mean", geom="point", shape=4, lwd=2)+
  theme(legend.position = "None",axis.text=element_text(size=8),
        axis.title=element_text(size=10))+
    xlab("")
}

nNA<-length(which(is.na(tab_OP$sea_state)==T))
if(nNA>0){cat(sprintf(lg[["1_missing_values"]],nNA,nrow_info))}

```

```{r, echo=FALSE,warning=FALSE,fig.cap=lg[['1_seabed_caption']],comment="",message=FALSE,fig.asp=0.5}

#fishing conditions /fishing operation : categorical variables
tab_OP2<- data %>% group_by(project,vessel_identifier,trip_code,station_number,gear_label)%>%
    summarize(seabed_features=unique(seabed_features),
              wind_cardinal_direction=unique(wind_cardinal_direction),diurnal_operation=unique(diurnal_operation))

nrow_info2<-nrow(tab_OP2)

if(length(which(is.na(tab_OP$seabed_features)==FALSE))>0){
ggplot(tab_OP2,aes(x=seabed_features,fill=gear_label))+ 
  geom_bar(stat = 'count',position="dodge",width=0.2) +
 labs(y =lg[["1_FO"]],x=lg[["1_seabed_labs"]])+
       theme_light()+
  theme(legend.position = "top")+#,axis.text=element_text(size=12),axis.title=element_text(size=14))
labs(fill=lg[["0_gear"]])
}

nNA<-length(which(is.na(tab_OP2$seabed_features)==T))
if(nNA>0){cat(sprintf(lg[["1_missing_values"]],nNA,nrow_info2))}

```



```{r, echo=FALSE,warning=FALSE,fig.cap=lg[['1_wind_dir_caption']],comment="",message=FALSE,fig.asp=0.5}

if(length(which(is.na(tab_OP2$wind_cardinal_direction)==FALSE))>0){
ggplot(tab_OP2,aes(x=wind_cardinal_direction,fill=gear_label))+ 
  geom_bar(stat = 'count',position="dodge",width=0.2) +
 labs(y = lg[["1_FO"]],x=lg[["1_wind_dir_labs"]])+
       theme_light()+
   theme(legend.position = "top")+#,axis.text=element_text(size=12),axis.title=element_text(size=14))
labs(fill=lg[["0_gear"]])
}

nNA<-length(which(is.na(tab_OP2$wind_cardinal_direction)==T))
if(nNA>0){cat(sprintf(lg[["1_missing_values"]],nNA,nrow_info2))}

```


```{r, echo=FALSE,warning=FALSE,fig.cap=lg[['1_day_caption']],comment="",message=FALSE,fig.asp=0.5}

tab_OP2$diurnal_operation<-factor(tab_OP2$diurnal_operation,levels=c("Y","N"),labels=c("Jour","Nuit"))

  
if(length(which(is.na(tab_OP2$diurnal_operation)==FALSE))>0){
ggplot(tab_OP2,aes(x=diurnal_operation,fill=gear_label))+ 
  geom_bar(stat = 'count',position="dodge",width=0.2) +
 labs(y = lg[["1_FO"]],x="")+
       theme_light()+
  theme(legend.position = "top")+#,axis.text=element_text(size=12),axis.title=element_text(size=14))
labs(fill=lg[["0_gear"]])
}

nNA<-length(which(is.na(tab_OP2$diurnal_operation)==T))
if(nNA>0){cat(sprintf(lg[["1_missing_values"]],nNA,nrow_info2))}

```


### `r lg[['1_subtitle_fishing_summary']]`

```{r, echo=FALSE,warning=FALSE,comment="",message=FALSE}

##Table of statistics for continuous variables only

varC<-c("fishing_duration","gear_depth","gear_speed","wind_force_beaufort","sea_state")

df<-data.frame(Variable=c(lg[["1_duration_labs"]],lg[["1_depth_labs"]],lg[["1_speed_labs"]],lg[["1_wind_labs"]],lg[["1_sea_state_labs"]])) 
df$min<-apply(tab_OP[,varC],2,"min",na.rm=T)
df$max<-apply(tab_OP[,varC],2,"max",na.rm=T)
df$mean<-apply(tab_OP[,varC],2,"mean",na.rm=T)
df$median<-apply(tab_OP[,varC],2,"median",na.rm=T)

df$diff<-data.frame(tab_OP) %>%
  summarize(fishing_duration=mean(fishing_duration[gear_label=="TEST"]-fishing_duration[gear_label=="STD"],na.rm=T),
            gear_depth=mean(gear_depth[gear_label=="TEST"]-gear_depth[gear_label=="STD"],na.rm=T),
            gear_speed=mean(gear_speed[gear_label=="TEST"]-gear_speed[gear_label=="STD"],na.rm=T),
            wind_force_beaufort=mean(wind_force_beaufort[gear_label=="TEST"]-wind_force_beaufort[gear_label=="STD"],na.rm=T),
            sea_state=mean(sea_state[gear_label=="TEST"]-sea_state[gear_label=="STD"],na.rm=T))%>%as.numeric()
  
  
df[,-1]<-round(df[,-1],1)

df$nNA<-apply(tab_OP[,varC],2,function(x){length(which(is.na(x)==TRUE))})

# #Pour la capture totale et le temps de tri
# var<-c("catch_weight","sorting_time")
# 
# df2<-data.frame(Variable=c("Poids de la capture (kg)","Durée de tri (min)"))  
# df2$min<-apply(tab_capture[,var],2,"min",na.rm=T)
# df2$max<-apply(tab_capture[,var],2,"max",na.rm=T)
# df2$mean<-apply(tab_capture[,var],2,"mean",na.rm=T)
# df2$median<-apply(tab_capture[,var],2,"median",na.rm=T)
# 
# df2[,-1]<-round(df2[,-1],1)
# df2$nNA<-apply(tab_capture[,var],2,function(x){length(which(is.na(x)==TRUE))})
# 
# df2$diff<-data.frame(tab_capture) %>%
#   summarize(catch_weight=mean(catch_weight[gear_label=="TEST"])-mean(catch_weight[gear_label=="STD"],na.rm=T),
#             sorting_time=mean(sorting_time[gear_label=="TEST"])-mean(sorting_time[gear_label=="STD"],na.rm=T))%>%as.numeric()
# 
# df<-rbind(df,df2)

if(sum(df$nNA>0)){
names(df)<-c("","Min","Max",lg[["1_mean"]],lg[["1_median"]],lg[["1_difference"]],lg[["1_values"]])

kable(df)
}else{df<-select(df,-nNA)
names(df)<-c("","Min","Max",lg[["1_mean"]],lg[["1_median"]],lg[["1_difference"]])
kable(df)
}


```


# 2. `r lg[['2_title']]`

## 2.1. `r lg[['2_1_subtitle']]`

### `r lg[['2_1_subtitle_catch_weight']]`

```{r, echo=FALSE,warning=FALSE,fig.cap=lg[['2_1_catch_caption']],comment="",message=FALSE}

#Comparison of catches weights, sorting time, discards weights / pair:

##sorting time calculation
data$sorting_start_date_time<-as.POSIXct(data$sorting_start_date_time,format="%Y-%m-%d %H:%M:%S")
data$sorting_end_date_time<-as.POSIXct(data$sorting_end_date_time,format="%Y-%m-%d %H:%M:%S")
data$sorting_time<-with(data,difftime(sorting_end_date_time,sorting_start_date_time,units="mins"))

#By catch
tab_capture<- data %>% 
  group_by(project,vessel_identifier,trip_code,station_number,gear_label)%>%
  summarize(catch_weight=unique(catch_weight),sorting_time=unique(sorting_time),
              discard_weight=unique(discard_weight))
nrow_info<- nrow(tab_capture)

if(length(which(is.na(tab_capture$catch_weight)==FALSE))>0){

  ggplot(tab_capture,aes(y=catch_weight,x=gear_label))+
          theme_light()+
  geom_boxplot(width=0.4,aes(fill=gear_label))+labs(y=lg[["2_1_catch_labs"]])+
   stat_summary(fun="mean", geom="point", shape=4, position = position_dodge(0.75),lwd=2)+
  theme(legend.position = "None",axis.text=element_text(size=8),
        axis.title=element_text(size=10))+
    xlab("")
}

nNA<-length(which(is.na(tab_capture$catch_weight)==T))
if(nNA>0){cat(sprintf(lg[["1_missing_values"]],nNA,nrow_info))}

```


### `r lg[['2_1_subtitle_sorting']]`

```{r, echo=FALSE,warning=FALSE,fig.cap=lg[['2_1_sorting_caption']],comment="",message=FALSE,fig.height=5}

if(length(which(is.na(tab_capture$sorting_time)==FALSE))>0){

  ggplot(tab_capture,aes(y=sorting_time,x=gear_label))+
          theme_light()+
  geom_boxplot(width=0.4,aes(fill=gear_label))+labs(y=lg[["2_1_sorting_labs"]])+
   stat_summary(fun="mean", geom="point", shape=4, position = position_dodge(0.75),lwd=2)+
  theme(legend.position = "None",axis.text=element_text(size=8),
        axis.title=element_text(size=10))+
    xlab("")
}
nNA<-length(which(is.na(tab_capture$sorting_time)==T))
if(nNA>0){cat(sprintf(lg[["1_missing_values"]],nNA,nrow_info))}


```

```{r, echo=FALSE,warning=FALSE,comment="",message=FALSE}

#a. For each FO and catch category, weight difference TEST-STD:
DIS_STD<-filter(tab_capture,gear_label=="STD")$sorting_time
DIS_TEST<-filter(tab_capture,gear_label=="TEST")$sorting_time

#Shapiro-Wilk test for normality
test1_STD<-tryCatch(shapiro.test(DIS_STD), error = function(e){"e"})
test1_TEST<-tryCatch(shapiro.test(DIS_TEST), error = function(e){"e"})

#b. Fisher test for equality of variances:
test1b<-tryCatch(var.test(DIS_STD,DIS_TEST), error = function(e){"e"})

if(class(test1_STD) =="htest" & class(test1_TEST) =="htest" & class(test1b) =="htest"){
  
  #If both tests not rejected => Student test:
  if(test1_TEST$p.value > 0.05 & test1_STD$p.value > 0.05 & test1b$p.value > 0.05){
    test2<-tryCatch(t.test(x=DIS_STD,y=DIS_TEST)  , error = function(e){"e"})
  }else{
    #Otherwise Mann-Whitney/Wilcoxon test:
    test2<-tryCatch(wilcox.test(DIS_STD,DIS_TEST, paired =FALSE, correct = TRUE, exact = FALSE), error = function(e){"e"})
  }


if(class(test2) == "htest"){#if no error
  
   if(test2$p.value<=0.05){
      
      cat(lg[["2_1_sorting_test_diff"]],"\n")
 }else{ cat(lg[["2_1_sorting_test_nodiff"]],"\n")}
      
}    
      
  pvalue<-round(test2$p.value,4)
  
  if(test1_TEST$p.value > 0.05 & test1_STD$p.value > 0.05 & test1b$p.value > 0.05){
    
    diff_DIS<-mean(DIS_TEST)-mean(DIS_STD)
    mean<-  abs(round(diff_DIS,3))
    sign<-c(lg[["2_1_less"]],lg[["2_1_more"]])[as.numeric(eval(diff_DIS>0))+1]
     
    cat(sprintf(lg[["2_1_sorting_test_mean"]],mean,sign,pvalue) )
        
        }else{
  
     diff_DIS<-median(DIS_TEST)-median(DIS_STD)
  
          med<-  abs(round(diff_DIS,3))
    sign<-c(lg[["2_1_less"]],lg[["2_1_more"]])[as.numeric(eval(diff_DIS>0))+1]
        cat(sprintf(lg[["2_1_sorting_test_med"]],med,sign,pvalue) )
 
      }
  
}

```



### `r lg[['2_1_subtitle_sorting_variation']]`

```{r, echo=FALSE,warning=FALSE,comment="",message=FALSE}

#Variation rate (TEST-STD)/STD

Tot_TEST<-sum(filter(tab_capture,gear_label=="TEST")$sorting_time)
Tot_STD<-sum(filter(tab_capture,gear_label=="STD")$sorting_time)

Var_Rate<-(Tot_TEST-Tot_STD)/Tot_STD*100

if(is.na(Var_Rate)==FALSE){
  sign<-c(lg[["2_1_decrease"]] ,lg[["2_1_increase"]])[as.numeric(eval(Var_Rate>0))+1]
  rate<-abs(round(Var_Rate,2))
cat(sprintf(lg[["2_1_sorting_var1"]],sign,rate))
}

```

### `r lg[['2_1_subtitle_discard_weight']]`

```{r, echo=FALSE,warning=FALSE,message=FALSE,fig.width=5}

if(length(which(is.na(tab_capture$discard_weight)==FALSE))>0){
ggplot(tab_capture,aes(y=discard_weight,x=gear_label,fill=gear_label))+
  geom_boxplot(width=0.5)+labs(y = lg[["2_1_discard_weight_labs"]])+
  xlab("Engin")+
          theme_light()+
    theme(legend.position = "None",axis.text=element_text(size=12),
        axis.title=element_text(size=14))+
  stat_summary(fun="mean", geom="point", shape=4, position = position_dodge(0.75),lwd=2)
}

```


```{r, echo=FALSE,warning=FALSE,comment="",message=FALSE}

#Discards difference TEST-STD:
DIS_STD<-filter(tab_capture,gear_label=="STD")$discard_weight
DIS_TEST<-filter(tab_capture,gear_label=="TEST")$discard_weight

#a. Shapiro-Wilk normality test
test1_STD<-tryCatch(shapiro.test(DIS_STD), error = function(e){"e"})
test1_TEST<-tryCatch(shapiro.test(DIS_TEST), error = function(e){"e"})

#b. Fisher test for variances equality:
test1b<-tryCatch(var.test(DIS_STD,DIS_TEST), error = function(e){"e"})

if(class(test1_STD) =="htest" & class(test1_TEST) =="htest" & class(test1b) =="htest"){
  
  #If both tests not rejected (p-value >0.05)=> Student test:
  if(test1_TEST$p.value > 0.05 & test1_STD$p.value > 0.05 & test1b$p.value > 0.05){
    test2<-tryCatch(t.test(x=DIS_STD,y=DIS_TEST)  , error = function(e){"e"})
  }else{
    #Otherwise Mann-Whitney/Wilcoxon test:
    test2<-tryCatch(wilcox.test(DIS_STD,DIS_TEST, paired =F, correct = T, exact = F), error = function(e){"e"})
  }
}

if(class(test2) == "htest"){#if no error
    
      if(test2$p.value<=0.05){
      
      cat(lg[["2_1_discard_test_diff"]],"\n")
 }else{ cat(lg[["2_1_discard_test_nodiff"]],"\n")}
      
}    
      
   pvalue<-round(test2$p.value,4)
  if(test1_TEST$p.value > 0.05 & test1_STD$p.value > 0.05 & test1b$p.value > 0.05){
    diff_DIS<-mean(DIS_TEST)-mean(DIS_STD)

    mean<-abs(round(diff_DIS,3))
    sign<-c(lg[["2_1_less"]],lg[["2_1_more"]])[as.numeric(eval(diff_DIS>0))+1]
    pvalue<-round(test2$p.value,4)
    cat(sprintf(lg[["2_1_discard_test_mean"]],mean,sign,pvalue))
      }else{
  
     diff_DIS<-median(DIS_TEST)-median(DIS_STD)
     med<-abs(round(diff_DIS,3))
    sign<-c(lg[["2_1_less"]],lg[["2_1_more"]])[as.numeric(eval(diff_DIS>0))+1]
 
    cat(sprintf(lg[["2_1_discard_test_med"]],med,sign,pvalue))
      }
   
```


### `r lg[['2_1_subtitle_discard_variation']]`

```{r, echo=FALSE,warning=FALSE,comment="",message=FALSE}

#Variation rate (TEST-STD)/STD
Tot_TEST<-sum(filter(tab_capture,gear_label=="TEST")$discard_weight)
Tot_STD<-sum(filter(tab_capture,gear_label=="STD")$discard_weight)

Var_Rate<-(Tot_TEST-Tot_STD)/Tot_STD*100
  
sign<-c(lg[["2_1_decrease"]] ,lg[["2_1_increase"]])[as.numeric(eval(Var_Rate>0))+1]
rate<-abs(round(Var_Rate,2))
cat(sprintf(lg[["2_1_discard_var1"]],sign,rate))


```



## 2.2. `r lg[["2_2_subtitle"]]`

### `r lg[["2_2_list_LAN"]]`

```{r, echo=FALSE,warning=FALSE,comment="",message=FALSE}
List_LAN<-unique(filter(data,catch_category=="LAN")$species)
cat(List_LAN,sep=", ")
```

### `r lg[["2_2_list_DIS"]]`

```{r, echo=FALSE,warning=FALSE,comment="",message=FALSE}
List_DIS<-unique(filter(data,catch_category=="DIS")$species)
cat(List_DIS,", ")
```

```{r, echo=FALSE,warning=FALSE,comment="",message=FALSE}
List_sp<-unique(data$species)

#Boxplot of landings/discards weights for each fishing operation: 

weight_species<-data %>% group_by(project,vessel_identifier,trip_code,station_number,gear_label,catch_category,species)%>%
 summarize(weight=sum(weight)*10^(-3))%>%as.data.frame()

weight_species<-as.data.frame(complete(weight_species,nesting(project,vessel_identifier,trip_code,station_number),gear_label,catch_category,species,fill=list(weight=0)))

#One plot by species
List_ggplot<-vector(mode="list",length=length(List_sp))

for(sp in 1:length(List_sp)){
  
  List_ggplot[[sp]]<-ggplot(filter(weight_species,species==List_sp[sp]),aes(y=weight,x=catch_category,fill=gear_label))+
    geom_boxplot()+labs(y = lg[["2_2_catch_labs"]])+ggtitle(List_sp[sp]) +
    stat_summary(fun="mean", geom="point", shape=4, position = position_dodge(0.75),lwd=2)+
    xlab("")+
       theme_light()+
    scale_x_discrete(labels=c(lg[["2_2_DIS"]],lg[["2_2_LAN"]]))+
    labs(fill = lg[["0_gear"]])
  print(List_ggplot[[sp]])
}

```


```{r, echo=FALSE,warning=FALSE,comment="",message=FALSE}

test_LAN<-matrix(NA,ncol=5,nrow=length(List_LAN))
row.names(test_LAN)<-List_LAN
test_LAN<-as.data.frame(test_LAN)

for(ii in 1:length(List_LAN)){
  
##For each species and catch category, paired test (STD/TEST) on the weights difference
#by catch
  test_LAN[ii,]<-f_test_unpaired(weight_species, List_LAN[ii],"LAN")
}
names(test_LAN)<-names(f_test_unpaired(weight_species, List_LAN[ii],"LAN"))

test_LAN$moyenne<-round(test_LAN$moyenne,2)
test_LAN$mediane<-round(test_LAN$mediane,2)

test_LAN$moyenne[test_LAN$test=="Fisher"]<-paste(test_LAN$moyenne[test_LAN$test=="Fisher"],"*",sep="")
test_LAN$mediane[test_LAN$test=="Kolmogorov"]<-paste(test_LAN$moyenne[test_LAN$test=="Kolmogorov"],"*",sep="")

test_LAN$pvalue[test_LAN$pvalue< 10^(-2)]<-"< 10-2"
test_LAN$pvalue[test_LAN$pvalue>0.1]<-">0.1"

names(test_LAN)<-c("p-value",lg[["2_2_mean_diff"]],lg[["2_2_median_diff"]],"Test",lg[["2_2_var1"]])


kable(test_LAN[,-c(4)],digits=2,caption=lg[["2_2_LAN_table_caption"]])

```

*`r lg[["2_2_DIS"]]`*
```{r, echo=FALSE,warning=FALSE,comment="",message=FALSE}

test_DIS<-matrix(NA,ncol=5,nrow=length(List_DIS))
row.names(test_DIS)<-List_DIS
test_DIS<-as.data.frame(test_DIS)

for(ii in 1:length(List_DIS)){
  #Test (H0) Diff_Poids=0 versus (H1) Diff_Poids not nul
  #+ Variation rate TEST/STD
  test_DIS[ii,]<-f_test_unpaired(weight_species, List_DIS[ii],"DIS")
}

names(test_DIS)<-names(f_test_unpaired(weight_species, List_DIS[ii],"LAN"))

test_DIS$pvalue[test_DIS$pvalue< 10^(-2)]<-"< 10-2"
test_DIS$pvalue[test_DIS$pvalue>0.1]<-">0.1"

test_DIS$moyenne<-round(test_DIS$moyenne,2)
test_DIS$mediane<-round(test_DIS$mediane,2)

test_DIS$moyenne[which(test_DIS$test=="Fisher")]<-paste(test_DIS$moyenne[which(test_DIS$test=="Fisher")],"*",sep="")
test_DIS$mediane[which(test_DIS$test=="Kolmogorov")]<-paste(test_DIS$moyenne[which(test_DIS$test=="Kolmogorov")],"*",sep="")

names(test_DIS)<-c("p-value",lg[["2_2_mean_diff"]],lg[["2_2_median_diff"]],"Test",lg[["2_2_var1"]])

kable(test_DIS[,-c(4)],digits=2,caption=lg[["2_2_DIS_table_caption"]])

```



# 3. `r lg[["3_title"]]`

### `r lg[["3_list_size"]]`

```{r, echo=FALSE,warning=FALSE,comment="",message=FALSE}

List_M<-unique(filter(data,is.na(number_at_length)==FALSE)$species)
cat(List_M,sep=", ")


```


### `r lg[["3_size_distribution"]]`

```{r, echo=FALSE,message=FALSE,warning=FALSE,comment="",message=FALSE,fig.width=18,fig.height=6}

List_E<-vector(mode="list",length=length(List_M))

for(sp in 1:length(List_M)){
  
  ##Size bounds for plots
  Taille_min<-min(filter(data,species==List_M[sp])$length_class)
  Taille_max<-max(filter(data,species==List_M[sp])$length_class)
  
  #x-Axis title
 unit<-unique(filter(data,species==List_M[sp])$length_code)
 type<-unique(filter(data,species==List_M[sp])$measure_type)

  if(type=="CL" | type=="LC"){
   Nom_Taille<-sprintf(lg[["3_CL_labs"]], unit) 
  }
  if(type=="TL" | type=="LT"){
     Nom_Taille<-sprintf(lg[["3_TL_labs"]], unit) 
  }
  
  Taille_com<-filter(min_length,species==List_M[sp])$min_length
  
  #Size counts in the catches
  length_ALL<-filter(data,species==List_M[sp]) %>%
  group_by(gear_label,length_class)%>%
    summarize(n=sum(elevated_number_at_length,na.rm=T))
  
 p1<-ggplot(data=length_ALL, aes(x=length_class, fill=gear_label)) +
      xlim(Taille_min,Taille_max)+
      geom_bar(stat='identity',aes(y=n),position = 'dodge')+
      theme_light()+
    labs(y = lg[["3_n_labs"]],x=Nom_Taille)+
     #facet_wrap(~Fraction, scales="fixed",ncol=3)+ # 1 plot par fraction
      geom_vline(xintercept=Taille_com,color="yellowgreen",size=1,linetype = "dashed")+
    theme(legend.position="bottom",legend.title = element_text(size=22),legend.text = element_text(size=22),axis.text=element_text(size=22),
        axis.title=element_text(size=24),plot.title = element_text(size = 26))+
        labs(fill=lg[["0_gear"]])+
    ylim(c(0,max(length_ALL$n)))+
   #ggtitle(paste0(List_M[sp]," (Total)"))  
    ggtitle(lg[["3_whole"]])
   
#  print(p)
  
  #Size counts by catch category
  length_cat<-filter(data,species==List_M[sp]) %>%
  group_by(gear_label,length_class,catch_category)%>%
    summarize(n=sum(elevated_number_at_length,na.rm=T))
  
  p2<-ggplot(data=filter(length_cat,catch_category=="LAN"), aes(x=length_class, fill=gear_label)) +
      xlim(Taille_min,Taille_max)+
      geom_bar(stat='identity',aes(y=n),position = 'dodge')+
      theme_light()+
    labs(y = lg[["3_n_labs"]],x=Nom_Taille)+
      geom_vline(xintercept=Taille_com,color="yellowgreen",size=1,linetype = "dashed")+
          theme(legend.position="bottom",legend.title = element_text(size=22),legend.text = element_text(size=22),axis.text=element_text(size=22),
        axis.title=element_text(size=24),plot.title = element_text(size = 26))+
        labs(fill=lg[["0_gear"]])+
        ylim(c(0,max(length_ALL$n)))+
     #ggtitle(paste0(List_M[sp]," (Débarquements)"))
        ggtitle(lg[["2_2_LAN"]])
  
  p3<-ggplot(data=filter(length_cat,catch_category=="DIS"), aes(x=length_class, fill=gear_label)) +
      xlim(Taille_min,Taille_max)+
      geom_bar(stat='identity',aes(y=n),position = 'dodge')+
      theme_light()+
    labs(y = lg[["3_n_labs"]],x=Nom_Taille)+
      geom_vline(xintercept=Taille_com,color="yellowgreen",size=1,linetype = "dashed")+
     theme(legend.position="bottom",legend.title = element_text(size=22),legend.text = element_text(size=22),axis.text=element_text(size=22),
        axis.title=element_text(size=24),plot.title = element_text(size = 26))+
    labs(fill=lg[["0_gear"]])+
        ylim(c(0,max(length_ALL$n)))+
        ggtitle(lg[["2_2_DIS"]])
  #   ggtitle(paste0(List_M[sp]," (Rejets)"))
  #print(p3)
  
   p<-ggarrange(p1,p2,p3,nrow=1,common.legend = T)
  
  cat(List_M[sp])

  print(p)
  
  ##List by species of escapment rates (STD-SEL)/STD: 
  #on the whole catch and lower/upper min_length.
  
  nSTD<-sum(filter(length_ALL,gear_label=="STD")$n,na.rm=T)
  nSEL<-sum(filter(length_ALL,gear_label=="TEST")$n,na.rm=T)
  taux_Total<-(nSTD-nSEL)/nSTD
  
  nSTD<-sum(filter(length_ALL,gear_label=="STD" & length_class >= Taille_com)$n,na.rm=T)
  nSEL<-sum(filter(length_ALL,gear_label=="TEST" & length_class >= Taille_com)$n,na.rm=T)
  taux_com<-(nSTD-nSEL)/nSTD
  
  nSTD<-sum(filter(length_ALL,gear_label=="STD" & length_class < Taille_com)$n,na.rm=T)
  nSEL<-sum(filter(length_ALL,gear_label=="TEST" & length_class < Taille_com)$n,na.rm=T)
  taux_HT<-(nSTD-nSEL)/nSTD
  
  tab_E<-data.frame(Espece=List_M[sp],taux_Total*100,taux_com*100,taux_HT*100)
  
  List_E[[sp]]<-tab_E

}


Tab_E<-bind_rows(List_E)

names(Tab_E)<-c(lg[["3_species"]],lg[["3_global"]],lg[["3_taille_com"]],lg[["3_undersize"]])

kable(Tab_E,digits=2,caption=lg[["3_escapement"]])
```


### `r lg[["3_selectivity_curve"]]`

```{r, echo=FALSE,warning=FALSE,comment="",message=FALSE,fig.asp=0.7}

for(sp in 1:length(List_M)){
  

  length_sp<-filter(data,species==List_M[sp]) %>% group_by(gear_label,length_class) %>%
  summarize(n=sum(elevated_number_at_length,na.rm=T)) %>%as.data.frame()
  
  #sel relative = TEST/TOTAL
  length_sp<-complete(length_sp,gear_label,length_class,fill=list(n=0))

  Rel_Sel<-length_sp %>% group_by(length_class)%>%
    summarize(rel_sel=n[gear_label=="TEST"]/sum(n),n_STD=sum(n[gear_label=="STD"]),n_TEST=sum(n[gear_label=="TEST"]))%>%as.data.frame()

  taille_com<-filter(min_length,species==List_M[sp])$min_length
    
   #x_title
 unit<-unique(filter(data,species==List_M[sp])$length_code)
 type<-unique(filter(data,species==List_M[sp])$measure_type)
  
  if(type=="CL" | type=="LC"){
      Nom_Taille<-sprintf(lg[["3_CL_labs"]], unit) 
   }
   if(type=="TL" | type=="LT"){
      Nom_Taille<-sprintf(lg[["3_TL_labs"]], unit) 
   }
 
  p<-ggplot(data=Rel_Sel)+
    geom_point(aes(x=length_class,y=rel_sel,size=n_STD+n_TEST))+
    guides(size=guide_legend(title = "n"))+
    xlab(Nom_Taille)+ylab(lg[["3_rel_selectivity"]])+
       theme_light()+
   geom_hline(yintercept=0.5, linetype="dashed", color = "grey")+
     geom_vline(xintercept=taille_com,size=1, linetype="dashed", color = "green")+
    ggtitle(List_M[sp])
  
  print(p)
  
}

```
