---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# {inser}

<!-- badges: start -->
[![pipeline status](https://forge.thinkr.fr/ifremer-lorient/inser/badges/main/pipeline.svg)](https://forge.thinkr.fr/ifremer-lorient/inser/-/commits/main)
[![coverage report](https://forge.thinkr.fr/ifremer-lorient/inser/badges/main/coverage.svg)](http://ifremer-lorient.pages.thinkr.fr/inser/coverage.html)
<!-- badges: end -->

The {inser} package generates a synthetic sheet of fishing gear selectivity indicators from 
catch comparison data. These data can be obtained from three types of experimental protocols: 
'twin', 'single paired' or 'independent' sampling for which a test gear is compared to a standard gear.

## Installation

In order to install the package you first need to create a gitlab token.

Go to User Settings > Access Tokens. 

Give your token an explicit name.

Choose no expiration date.

Choose `api` as scope.

Save your token in your .Renviron file. (`usethis::edit_r_environ()`) like so:

```
FORGE_THINKR_TOKEN=<put your gitlab token here>
```

Then run this code:

```{r, eval=FALSE}
install.packages(c("git2r", "remotes"))

options(
  remotes.git_credentials = git2r::cred_user_pass(
    username = "gitlab-ci-token", 
    password = Sys.getenv("FORGE_THINKR_TOKEN")
  )
)

remotes::install_git("https://forge.thinkr.fr/ifremer-lorient/inser/")
```

## Package Documentation

The package documentation website can be found here: https://ifremer-lorient.pages.thinkr.fr/inser/
