---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# {inser}

<!-- badges: start -->
[![R-CMD-check](https://github.com/mariemorfin/inser/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/mariemorfin/inser/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The {inser} package generates a synthetic sheet of fishing gear selectivity indicators from 
catch comparison data. These data can be obtained from three types of experimental protocols: 
'twin', 'single paired' or 'independent' sampling for which a test gear is compared to a standard gear.

## Installation

You can install the development version of {inser} from GitHub with:

```{r, eval=FALSE}
remotes::install_github("mariemorfin/inser")
```

## Package Documentation

The package documentation website can be found here: https://mariemorfin.github.io/inser/
