---
title: "Dev history - Deliverables"
output: 
  html_document:
    toc: true
    toc_depth: 1
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  eval = FALSE
  )
```

In this document, you will find useful steps/commands to integrate new deliverables to your package (pkgdown, gitdown, testdown, dockerfile, ...)

# Try installation from GitLab

```{r}
if (!requireNamespace("git2r")) { install.packages("git2r")}
username <- rstudioapi::showPrompt("username", "Please enter your git username:", "name")
password <- rstudioapi::askForPassword()
remotes::install_gitlab(
  repo = "https://forge.thinkr.fr/thinkr/missions/<project>",
  credentials = git2r::cred_user_pass(username, password))
```


# Deliverables

### renv data - If you deliver a package with a project inside ----

```{r}
rstudioapi::navigateToFile("dev/flat_user_project.Rmd")
```

### Create a `deliverables` dir

```{r}
dir.create("deliverables")
usethis::use_build_ignore("deliverables")
usethis::use_git_ignore("deliverables")
```

### Upgrade version Number in DESCRIPTION
```{r}
usethis::use_version(which = c("major", "minor", "patch", "dev")[2])
```

### Upgrade version number in README and knit
```{r}
rstudioapi::navigateToFile('README.Rmd')
# rstudioapi::navigateToFile("inst/rsproject/README.md")
```

### Update NEWS.md
```{r}
rstudioapi::navigateToFile("NEWS.md")
```

### Create a commit for the version

### Add tag on version commit

### Update description files in Shiny app

```{r}
papillon::create_pkg_biblio_file(
  to = "html",
  out.dir = "inst/app/www/about", edit = FALSE)

papillon::create_pkg_desc_file(
  source = c("archive"),
  out.dir = "inst/app/www/about", to = "html", edit = FALSE)
```

### Update Readme using (and knit)
```{r}
papillon::create_pkg_desc_file(source = c("archive"),
                                out.dir = tempdir(), to = "raw",
                                edit = TRUE)
```


## covr

```{r}
x <- covr::package_coverage()
```

#### Change {my-project}

```{r}
covr::report(x, file = "deliverables/codecoverage/codecoverage-full-report.html")
```

#### Add read information
```{r}
file.copy(from = "dev/codecoverage_explanation.md",
          to = "deliverables", overwrite = TRUE)
```

#### add covrpage

```{r}
# remotes::install_github("metrumresearchgroup/covrpage")
covrpage::covrpage(vignette = TRUE)
file.remove("tests/README.md")
```

## Vignettes

#### add last_modif files
```{r}
# remotes::install_github("ThinkR-open/gitdown")
gitdown::create_vignette_last_modif()
rstudioapi::navigateToFile("vignettes/modification_files.Rmd")
```


## pkgdown

```{r}
# _Pkgdown - Pas besoin d'inclure le pkgdown pour un projet open-source avec un gh-pages
usethis::use_pkgdown()

# remotes::install_github("ThinkR-open/papillon")
# remotes::install_github("ThinkR-open/thinkrtemplate")
# remotes::install_github("r-lib/pkgdown", ref = "v1.3.0")
# papillon::open_pkgdown_function(path = "docs")
devtools::install(upgrade = "never")
usethis::use_git_ignore("deliverables/pkgdown/")
usethis::use_git_ignore("pkgdown/")
papillon::build_pkgdown(
  lazy = TRUE,
  yml = system.file("pkgdown/_pkgdown.yml", package = "lozen"),
  favicon = system.file("pkgdown/favicon.ico", package = "lozen"),
  move = TRUE, clean_before = TRUE, preview = FALSE
)
down_dir <- "deliverables/pkgdown"
unlink(down_dir, recursive = TRUE)
file.copy("inst/docs", "deliverables", recursive = TRUE)
file.rename("deliverables/docs", down_dir)
unlink("inst/docs", recursive = TRUE)
browseURL("deliverables/pkgdown/index.html")
```


## Gitdown

=> Create deliverable commit

```{r}
# remotes::install_github("ThinkR-open/gitdown", upgrade = "never")
# remotes::install_github("ThinkR-open/gitdown", upgrade = "never", ref = "report-links")
# remotes::install_github("ThinkR-open/gitdown", upgrade = "never", ref = "add_history_files")
gitdown::git_down(
  pattern = c("Issues" = "#[[:digit:]]+"),
  author = "Sébastien Rochette, ThinkR; Margot Brard, ThinkR",
  ref = "main")

# rmarkdown::render("gitdown/index.Rmd")
```


#### Git issues names

Connect as a fixed user to a gitlab instance

```{r}
# remotes::install_github("statnmap/gitlabr", upgrade = "never")
library(gitlabr)
library(dplyr)
my_project <- gl_project_connection(
  gitlab_url = "https://forge.thinkr.fr",
  project = 317, #repo.rtask",
  private_token = Sys.getenv("FORGE_THINKR_TOKEN")
)
my_project_issues <- my_project(gl_list_issues)

# install.packages("writexl")
writexl::write_xlsx(my_project_issues, "deliverables/issues_description.xlsx")

my_pattern_table <- my_project_issues %>%
  mutate(
    pattern = paste0("#", iid),
    title = paste(pattern, title)
  ) %>%
  select(pattern, title)

gitdown::git_down(
  pattern = c("Issues" = "#[[:digit:]]+"
  ),
  pattern.table = my_pattern_table,
  author = "Sébastien Rochette, ThinkR",
  ref = "add-project")
# ref = "origin/dev")

down_dir <- "deliverables/gitdown"
unlink(down_dir, recursive = TRUE)
file.copy("gitdown", "deliverables", recursive = TRUE)
unlink("gitdown", recursive = TRUE)
```


## Testdown

```{r}
# remotes::install_github("ThinkR-open/testdown")
# remotes::install_github("ThinkR-open/testdown", ref = "escape-html")
testdown::test_down()
down_dir <- "deliverables/testdown"
unlink(down_dir, recursive = TRUE)
file.copy("tests/testdown", "deliverables", recursive = TRUE)
unlink("tests/testdown", recursive = TRUE)
```

## Userguide as PDF

#### Définition d'un dossier temporaire
```{r}
my_tmp <- tempdir()
```

#### Création des fichiers dans le dossier
```{r}
lozen::thinkR_pdf_create_header(
  path_here = my_tmp,
  author = "Sébastien Rochette",
  title = "ListOfCodes Userguide",
  description = "The userguide of the Shiny application",
  email = "contact@thinkr.fr",
  lang = "en"
)
```

#### Création du PDF en ligne de commande
```{r}
input <- "vignettes/cc-userguide.Rmd"
tmp_output <- "vignettes/temp.Rmd"
```


#### Amend YAML to add PDF options

```{r}
lozen::amend_yaml_pdf_output(
  input, output_file = tmp_output, lang = "en")
```


#### Render with output_options

```{r}
rmarkdown::render(tmp_output,
                  output_dir = "deliverables",
                  output_file = "userguide.pdf",
                  output_format = "bookdown::pdf_book",
                  output_options =
                    list(toc = TRUE,
                         toc_depth = 3,
                         highlight = "tango",
                         includes = list(
                           before_body = file.path(my_tmp, "before_body.tex"),
                           in_header = file.path(my_tmp, "header.tex")),
                         keep_tex = FALSE,
                         number_sections = TRUE

                    )
)
```

#### Remove temporary Rmd
```{r}
file.remove(tmp_output)
file.remove("vignettes/userguide.log")
```


## DockerFile and sources

```{r}
dir.create("deliverables/installation/")
```

#### Verify Dockerfile in "deliverables/installation/Dockerfile"

```{r}
usethis::use_git_ignore("deliverables/installation/Dockerfile_golem")
golem::add_dockerfile(
  output = "deliverables/installation/Dockerfile_golem",
  from = "rocker/verse:3.5.2"
)
unlink("R/app_config.R")
unlink("inst/golem-config.yml")
unlink(".dockerignore")
```

#### Set MRAN
```{r}
# dockerlines <- readLines("deliverables/installation/Dockerfile")
```

#### Modify {golem} commit
```{r}
# dockerlines[grep("golem", dockerlines)] <-
#   "RUN R -e 'remotes::install_github(\"ThinkR-open/golem@a4daea84f04de30cd80fe9fe80ce5afd74be87b3\")'"
```

#### New lines at the beginning
```{r}
# addlines <- c(
# "# CRAN on: 14-01-2019",
# "RUN echo \"options(repos = list(CRAN = 'https://packagemanager.rstudio.com/cran/136'))\" >> /usr/local/lib/R/etc/Rprofile.site"
# )
#
# newdockerfile <- c(dockerlines[1], addlines, dockerlines[2:length(dockerlines)])
# writeLines(enc2utf8(newdockerfile), "deliverables/installation/Dockerfile")
```


#### Create sources
```{r}
usethis::use_git_ignore("deliverables/sources/")
dir.create("deliverables/sources")
devtools::build(path = "deliverables/sources/")
```


#### Add sources along the Dockerfile for Shiny Apps
```{r}
dir.create("deliverables/installation")
usethis::use_git_ignore("deliverables/installation/*.tar.gz")
file.remove(list.files("deliverables/installation", pattern = ".tar.gz", full.names = TRUE))
file.copy(tail(list.files("deliverables/sources", pattern = ".tar.gz", full.names = TRUE), 1),
          to = "deliverables/installation")
```


#### Update installation guide with last version delivered
#### Vignette: cc_installation_guide.Rmd
