---
title: "flat_utils_selectivity_sheet.Rmd empty"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
```

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

```{r pkg}
library(ggplot2)
```


# Translating selectivity sheets

## `create_translate_dict()` : generate object with translated text

This function will provide all the necessary text to generate the selectivity sheet in the required language. The text is stored in a named list that will be accessible when calling the `create_selectivity_sheet()` function.

```{r function-create_translate_dict}
#' create_translate_dict
#' 
#' Create a list with all the text elements of the selectivity sheet in the selected language
#'
#' @param path character. The path to the csv translation file
#' @param language character. The chosen language for the text, must be "FR" or "EN" (default)
#' @param encoding character. The encoding of the csv file, default to "UTF-8"
#' @param sep character. The field separator used in the CSV file
#' 
#' @importFrom glue glue
#' @importFrom tools file_ext
#' @importFrom stats setNames
#' @importFrom utils read.csv
#' 
#' @return list. A list of translated text, with names referring to their location in the sheet
#' @export
create_translate_dict <- function(path = system.file("template", "translation.csv", package = "inser"),
                                  language = c("EN", "FR"),
                                  encoding = "UTF-8",
                                  sep = ";") {
  # check selected language
  language <- match.arg(language)
  
  # check translation file exist
  if (isFALSE(file.exists(path))) {
    stop(glue("Translation file {path} not found"))
  }
  
  # check if translation file is a csv
  if (isTRUE(file_ext(path) != "csv")) {
    stop(glue("Translation file {path} is not a csv file"))
  }
  
  # read csv and extract language as named list
  translator <- read.csv(file = path,
                         encoding = encoding,
                         sep = sep)
  
  translator <- setNames(object = translator[[language]],
                         nm = as.character(translator[["id"]])
                         )
  
  # warn user of the translation being used
  message(glue("Using the {language} version of the selectivity template"))
  
  # return list
  return(translator)
}
```

```{r examples-create_translate_dict}
# create the EN translator
lg <- create_translate_dict(language = "EN")

# call main title by its ID
cat(lg[["0_main_title"]])

# create the FR translator
lg <- create_translate_dict(language = "FR")

# call main title by its ID
cat(lg[["0_main_title"]])
```

Once the translation list object is loaded in the environment, we can call it inside Rmd chunks to display the correct text. We can call this translator at several places, as explained below.

* **Translating file title and subtitle**
  - edit yaml header
  - _example_ : c.f. chunk below
  
```{r vign-header, eval = FALSE, echo = TRUE}
---
title: "`r lg[['0_main_title']]`"
subtitle: "`r lg[['0_sub_title_twin']]`"
output: word_document
---
```

* **Translating chapter and text**
  - use inline r evaluation code
  - _example_ : `` `r
lg[['0_main_title']]` `` will be shown in the text as : `r lg[['0_main_title']]`

<!-- line break in r inline code prevents it to be evaluated so we can show the verbatim -->

* **Translating graph caption and labels**
  - use direct call to the list object
  - _example_ :
      - using `fig.cap = lg[['1_duration_caption']]` in chunk header will render the proper plot caption
      - using `labs(y = lg[["1_duration_labs"]])` in the ggplot construction will render the proper plot label
  
```{r vign-data, include=FALSE}
# load example dataset with missing fishing duration
tab_OP <- structure(
  list(
    project = c("InseR", "InseR", "InseR", "InseR","InseR", "InseR"),
    vessel_identifier = c("vessel1","vessel1","vessel1","vessel1","vessel1","vessel1"),
    trip_code = c(3,3, 3, 3, 3, 3),
    station_number = c(3L, 5L, 8L, 10L, 13L, 14L),
    fishing_duration = c(3.75, 4, 3, 4, 3, 4),
    gear_depth = c(99L, 104L, 103L, 99L, 97L, 93L),
    wind_force_beaufort = c(4L,5L, 5L, 4L, 4L, 3L),
    gear_speed = c(3.5,3.5,3.40000009536743,3.40000009536743,3.70000004768372,4),
    sea_state = c(4L,5L, 5L, 4L, 4L, 3L)
  ),
  class = "data.frame",
  row.names = c(NA, -6L)
)
```

```{r vign-graph, echo = TRUE, fig.cap = lg[['1_duration_caption']]}
ggplot(tab_OP, aes(y = fishing_duration)) +
  geom_boxplot(width = 0.5) +
  labs(y = lg[["1_duration_labs"]])
```

* **Translating text outputs**
  - prefer the use of `sprintf()` instead of `paste0()` to enable the text to be provided as a single character line
  - _example_ : c.f. chunk below

```{r vign-sprintf}
# Get dummy variable values
nNA <- 2
nrow_info <- 10

# the sprintf character loaded is : "Note : il manque %i valeurs sur les %i opérations de pêche."

# Generate message with sprintf and lg object
if(nNA>0){
  cat(sprintf(lg[["1_missing_values"]], nNA, nrow_info))
}
```
  

* **Rendering report**
  - Once the report is correctly including the calls to the translation object, we can render it with `rmarkdown::render()`
  - Language of rendering will depend on the pre-loaded translation object
  - _example_ : c.f. chunk below rendering the example `selectivity_sheet_template.Rmd` file in both EN and FR
  
> The path to the template and its docx outputs can be retrieved with `system.file("template", package = "inser")`.

```{r vign-render}
# select template file
template_file <- system.file("template","selectivity_sheet_template.Rmd", package = "inser")

# load EN translation object
lg <- create_translate_dict(language = "EN")

# render template (will generate EN report)
rmarkdown::render(input = template_file,
       output_file = "selectivity_sheet_en.docx",
       quiet = TRUE)

# create the FR translator
lg <- create_translate_dict(language = "FR")

# render template (will generate FR report)
rmarkdown::render(input = template_file,
       output_file = "selectivity_sheet_fr.docx",
       quiet = TRUE)
```


```{r tests-create_translate_dict}
test_that("create_translate_dict works", {

  # create csv with wrong extension
  output_dir <- tempfile(pattern = "translate_dict")
  dir.create(output_dir)
  file.copy(from = system.file("template", "translation.csv", package = "inser"),
            to = file.path(output_dir, "notacsvfile.txt"))
  bad_ext_file <- file.path(output_dir, "notacsvfile.txt")
  
  #' @description Test `create_translate_dict` returns error for incorrect csv or language
  expect_error(
    object = create_translate_dict(path = "notaexistingfile"),
    regexp = "Translation file notaexistingfile not found"
    )
  expect_error(
    object = create_translate_dict(
      path = bad_ext_file
      ),
    regexp = glue::glue("Translation file {bad_ext_file} is not a csv file")
    )
  expect_error(
    object = create_translate_dict(
      language = "IT"
    ),
    regexp = "\\'arg\\' should be one of .EN., .FR."
  )
  
  # run function for EN and FR output (testing both upper and lower case)
  en_output <- create_translate_dict(language = "EN")
  fr_output <- create_translate_dict(language = "FR")
  
  #' @description Test english output of `create_translate_dict`
  expect_equal(object = en_output[["0_test_entry"]],
               expected = "This is the text output of the example entry")
  expect_equal(object = fr_output[["0_test_entry"]],
               expected = "Ceci est la sortie de texte de l'entrée d'exemple")
  
  # clean
  unlink(output_dir,recursive = TRUE)
})
```


```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_utils_selectivity_sheet.Rmd",
               vignette_name = "Manage selectivity sheet content",
               overwrite = TRUE,
               check = FALSE)
```

